---
title: "ABL_kinasefunction_data_parser"
author: "Haider Inam"
date: '2023-08-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = normalizePath(".."))

library(stringr)
library(dplyr)
library(ggplot2)
library(plotly)
library(tictoc)
library(doParallel)
library(foreach)
library(RColorBrewer)
library(ggpubr)

# 

```

```{r}
#Cleanup code for plotting
source("code/plotting/cleanup.R")
```

#8.30.23
#The following code was taken from ABL_SM_CRISPR_Cut_Analyses.Rmd
#Essentially all this code does is that it takes two BaF3 ABL Region 1 D0 samples and two D6 samples, and creates a dataframe with enrichment scores.
#Ivan wanted counts from separate D0 backgrounds, and he wanted every mutant, regardless of whether it was seen in both baseline samples (when I do analyses, I take out any mutant that is not seen in both baseline samples). Let's call these "unseen mutants"
#This code does not include unseen mutants by default. To make sure that unseen mutants are seen, uncomment out the Ivan section in compare_screens.R. Once you uncomment it, then run the code below
#One more note: this is Region 1 (Amino acids 242-322) data from Lane 18 only. In the future you can include samples from other lanes.

```{r}
source("code/compare_screens.R")

source("code/plotting/cleanup.R")
source("code/plotting/heatmap_plotting_function.R")
# rm(list=ls())

comparisons=read.csv("data/Consensus_Data/novogene_lane18/TwistRegion1Screen_Comparisons_Todo.csv")
# comparisons=comparisons%>%filter(Completed%in%"FALSE")

# for(i in 1:nrow(comparisons)){
  i=10
  dirname=comparisons$dirname[i]
  pathname=paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,sep = "")
  # Create directory if it doesn't already exist
  if (!file.exists(pathname)){
    dir.create(pathname)
} 
before_screen1_identifier=unlist(strsplit(comparisons$before_screen1_identifier[i],","))
after_screen1_identifier=unlist(strsplit(comparisons$after_screen1_identifier[i],","))
before_screen2_identifier=unlist(strsplit(comparisons$before_screen2_identifier[i],","))
before_screen2_identifier="BTRID0_FT"
after_screen2_identifier=unlist(strsplit(comparisons$after_screen2_identifier[i],","))
  # length(after_screen1_identifier)
# screen_compare_means=compare_screens(comparisons$before_screen1_identifier[i],
#                                      comparisons$after_screen1_identifier[i],
#                                      comparisons$before_screen2_identifier[i],
#                                      comparisons$after_screen2_identifier[i])
screen_compare_means=compare_screens(before_screen1_identifier,
                                     after_screen1_identifier,
                                     before_screen2_identifier,
                                     after_screen2_identifier)

screen_compare_means_forexport=apply(screen_compare_means,2,as.character)
# dirname
# write.csv(screen_compare_means_forexport,file="output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2ft.csv")

# Plot 1. What does the heatmap look like from the average of the net growth rate?
heatmap_plotting_function(screen_compare_means,242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot1_heatmap.pdf",sep=""),width=10,height=6,units="in",useDingbats=F)
# screen_compare_means2=screen_compare_means%>%filter(alt_codon%in%twist$Codon)

# Plot 2a: What do the correlations look like for net growth rate (show mutants in text)?

ggplot(screen_compare_means,aes(x=netgr_obs_screen1,y=netgr_obs_screen2,color=resmuts,label=species))+geom_text(size=2.5)+geom_abline()+cleanup+stat_cor(method = "pearson")+labs(color="Known\nResistant\nMutant")+scale_x_continuous("Net growth rate screen 1")+scale_y_continuous("Net growth rate screen 2")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2a_Netgrowthrate_correlations_text.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

# Plot 2b: What do the correlations look like for enrichment scores (show mutants in points)?
ggplot(screen_compare_means,aes(x=netgr_obs_screen1,y=netgr_obs_screen2,label=species))+geom_point(color="black",shape=21,size=2,aes(fill=resmuts))+geom_abline()+cleanup+stat_cor(method = "pearson")+labs(fill="Known\nResistant\nMutant")+scale_x_continuous("Net growth rate screen 1")+scale_y_continuous("Net growth rate screen 2")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2b_Netgrowthrate_correlations_points.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)
# Plot 2c: What do the correlations look like for enrichment scores (show mutants in text)?
ggplot(screen_compare_means,aes(x=score_screen1,y=score_screen2,color=resmuts,label=species))+geom_text(size=2.5)+geom_abline()+cleanup+ stat_cor(method = "pearson")+labs(color="Known\nResistant\nMutant")+scale_x_continuous("Enrichment score screen 1")+scale_y_continuous("Enrichment score screen 2")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2c_Enrichmentscores_correlations_text.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

# Plot 3a: Plots: what are the overall net growth rate distributions?
ggplot(screen_compare_means,aes(x=netgr_obs_mean,fill=resmuts))+geom_density(alpha=0.7)+cleanup+labs(fill="Known\nResistant\nMutant")+scale_x_continuous("Mean net growth rate of screens")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot3a_Netgrowthrate_distributions_resmuts.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)
# Plot 3b: Plots: what are the net growth rate distributions?

library(reshape2)
screen_compare_melt=melt(screen_compare_means%>%dplyr::select(species,netgr_obs_screen1,netgr_obs_screen2),id.vars = "species",measure.vars =c("netgr_obs_screen1","netgr_obs_screen2"),variable.name = "Condition",value.name = "netgr_obs")


ggplot(screen_compare_melt,aes(x=netgr_obs,fill=Condition))+
  geom_density(alpha=0.7)+
  cleanup+
  scale_x_continuous("Net growth rate observed")+
  scale_fill_discrete(labels=c("Screen 1","Screen 2"))
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot3b_Netgrowthrate_distributions.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

# }

# dirname="K562_Medium_rep1vs2"

```
