---
title: "ABL_region1_parser"
author: "Haider Inam"
date: '2023-03-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath(".."))

library(stringr)
library(dplyr)
library(ggplot2)
library(plotly)
library(tictoc)
library(doParallel)
library(foreach)
library(RColorBrewer)
library(ggpubr)
library(pROC)
# 

```

```{r}
#Cleanup code for plotting
source("code/plotting/cleanup.R")
source("code/cosmic_data_adder.R")
source("code/compare_screens.R")
source("code/compare_screens_archive.R")
source("code/compare_screens_twosamples.R")
source("code/merge_samples_twosamples.R")
source("code/plotting/heatmap_plotting_function.R")
```
### Data parsing  

```{r,eval=F}
source("code/variantcaller/add_l298l.R")
for(i in c(1:18)){
  sample=paste("sample",i,sep = "")
  # sample="sample1"
  
  input_df_nol298l=read.csv(paste("data/Consensus_Data/novogene_lane18/",sample,"/nol298l/duplex/variant_caller_outputs/variants_unique_ann.csv",sep=""))
  input_df_l298l=read.csv(paste("data/Consensus_Data/novogene_lane18/",sample,"/l298l/duplex/variant_caller_outputs/variants_unique_ann.csv",sep=""))
  
  output_df=add_l298l(input_df_nol298l,input_df_l298l)
  write.csv(output_df,
            paste("data/Consensus_Data/novogene_lane18/",sample,"/duplex/variant_caller_outputs/variants_unique_ann.csv",sep = ""))  
}

input_df_nol298l=read.csv("data/Consensus_Data/novogene_lane18/sample9/nol298l/duplex/variant_caller_outputs/variants_unique_ann.csv")
input_df_l298l=read.csv("data/Consensus_Data/novogene_lane18/sample9/l298l/duplex/variant_caller_outputs/variants_unique_ann.csv")
  
output_df=add_l298l(input_df_nol298l,input_df_l298l)
write.csv(output_df,"data/Consensus_Data/novogene_lane18/sample9/duplex/variant_caller_outputs/variants_unique_ann.csv")  

```

```{r, eval=F}

# rm(list=ls())
cellcounts_matrix_dir="data/Consensus_Data/novogene_lane18/TwistRegion1Screen_CellCounts_Matrix.csv"
comparisons=read.csv("data/Consensus_Data/novogene_lane18/TwistRegion1Screen_Comparisons_Todo.csv")
# comparisons=comparisons%>%filter(Completed%in%"FALSE")

for(i in 1:nrow(comparisons)){
# for(i in 1:1){
  # i=1
  dirname=comparisons$dirname[i]
  pathname=paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,sep = "")
  # Create directory if it doesn't already exist
  if (!file.exists(pathname)){
    dir.create(pathname)
} 
before_screen1_identifier=unlist(strsplit(comparisons$before_screen1_identifier[i],","))
after_screen1_identifier=unlist(strsplit(comparisons$after_screen1_identifier[i],","))
before_screen2_identifier=unlist(strsplit(comparisons$before_screen2_identifier[i],","))
after_screen2_identifier=unlist(strsplit(comparisons$after_screen2_identifier[i],","))
  # length(after_screen1_identifier)
# screen_compare_means=compare_screens(comparisons$before_screen1_identifier[i],
#                                      comparisons$after_screen1_identifier[i],
#                                      comparisons$before_screen2_identifier[i],
#                                      comparisons$after_screen2_identifier[i])
screen_compare_means=compare_screens_archive(before_screen1_identifier,
                                     after_screen1_identifier,
                                     before_screen2_identifier,
                                     after_screen2_identifier,
                                     cellcounts_matrix_dir)
# Adding a flag,"depleted", for when a mutant completely drops out of a screen in both replicates
screen_compare_means=screen_compare_means%>%mutate(depleted=case_when(ct_screen1_after%in%0.5&&ct_screen2_after%in%0.5~"TRUE",
                                                                      T~"FALSE"))



screen_compare_means_forexport=apply(screen_compare_means,2,as.character)
write.csv(screen_compare_means_forexport,file = paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/screen_comparison_",dirname,".csv",sep=""))

start_site=240
end_site=322
# Plot 1. What does the heatmap look like from the average of the net growth rate?
heatmap_plotting_function(screen_compare_means%>%filter(is_intended%in%1),242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")
ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot1_heatmap.pdf",sep=""),width=10,height=6,units="in",useDingbats=F)

# Plot 2a: What do the correlations look like for net growth rate (show mutants in text)?

ggplot(screen_compare_means%>%filter(is_intended%in%1),aes(x=netgr_obs_screen1,y=netgr_obs_screen2,color=resmuts,label=species))+geom_text(size=2.5)+geom_abline()+cleanup+stat_cor(method = "pearson")+labs(color="Known\nResistant\nMutant")+scale_x_continuous("Net growth rate screen 1")+scale_y_continuous("Net growth rate screen 2")
ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2a_Netgrowthrate_correlations_text.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

# Plot 2b: What do the correlations look like for enrichment scores (show mutants in points)?
ggplot(screen_compare_means%>%filter(is_intended%in%1),aes(x=netgr_obs_screen1,y=netgr_obs_screen2,label=species))+geom_point(color="black",shape=21,size=2,aes(fill=resmuts))+geom_abline()+cleanup+stat_cor(method = "pearson")+labs(fill="Known\nResistant\nMutant")+scale_x_continuous("Net growth rate screen 1")+scale_y_continuous("Net growth rate screen 2")
ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2b_Netgrowthrate_correlations_points.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)
# Plot 2c: What do the correlations look like for enrichment scores (show mutants in text)?
ggplot(screen_compare_means%>%filter(is_intended%in%1),aes(x=score_screen1,y=score_screen2,color=resmuts,label=species))+geom_text(size=2.5)+geom_abline()+cleanup+ stat_cor(method = "pearson")+labs(color="Known\nResistant\nMutant")+scale_x_continuous("Enrichment score screen 1")+scale_y_continuous("Enrichment score screen 2")
ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2c_Enrichmentscores_correlations_text.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)


# Plot 2d: What do the correlations look like for net growth rates (show mutants in text + add depleted flag)?
ggplot(screen_compare_means%>%filter(is_intended%in%1,protein_start%in%c(start_site:end_site)),aes(x=netgr_obs_screen1,y=netgr_obs_screen2,label=species))+geom_point(color="black",shape=21,size=2,aes(fill=depleted),alpha=.7)+geom_abline()+cleanup+stat_cor(method = "pearson")+labs(fill="Depleting\nMutant")+scale_x_continuous("Net growth rate screen 1")+scale_y_continuous("Net growth rate screen 2")
ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2d_Netgrowthrate_correlations_depletedmutants_points.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

# Plot 3a: Plots: what are the overall net growth rate distributions?
ggplot(screen_compare_means%>%filter(is_intended%in%1),aes(x=netgr_obs_mean,fill=resmuts))+geom_density(alpha=0.7)+cleanup+labs(fill="Known\nResistant\nMutant")+scale_x_continuous("Mean net growth rate of screens")
ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot3a_Netgrowthrate_distributions_resmuts.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)
# Plot 3b: Plots: what are the net growth rate distributions?

library(reshape2)
screen_compare_melt=melt(screen_compare_means%>%dplyr::select(species,netgr_obs_screen1,netgr_obs_screen2),id.vars = "species",measure.vars =c("netgr_obs_screen1","netgr_obs_screen2"),variable.name = "Condition",value.name = "netgr_obs")


ggplot(screen_compare_melt,aes(x=netgr_obs,fill=Condition))+
  geom_density(alpha=0.7)+
  cleanup+
  scale_x_continuous("Net growth rate observed")+
  scale_fill_discrete(labels=c("Screen 1","Screen 2"))
ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot3b_Netgrowthrate_distributions.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

}

# dirname="K562_Medium_rep1vs2"

```

### Solvent accessibility fitness scores  
  
Doing some quick analyses on buried hydrophobic vs exposed residues

Quick analysis to do on the secondary structure:
The buried hydrophobic core is probably going to be more susceptible to polar/hydrophilic substitutions, and not as much to hydrophobic substitutions... do you see that in the il3 independence data? Answer: yes, I see a slight singal but it's not huge
```{r}
dssp=read.csv("data/DSSP_SolventAccessibility_ABL/2hyy_dspp.csv",header = T)
dssp=dssp%>%mutate(RESIDUE=as.numeric(RESIDUE),
                   ACC=as.numeric(ACC),AA=gsub("<ca>","",AA),
                   SS=case_when(STRUCTURE%in%c("E","B")~"b-sheet",
                                STRUCTURE%in%c("H","G","I")~"a-helix",
                                STRUCTURE%in%"T"~"turn",
                                T~"undefined"))%>%dplyr::select(-"STRUCTURE")

dssp=dssp%>%rename(protein_start=RESIDUE)

il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%dplyr::select(species,protein_start,netgr_obs_mean)
il3=il3%>%group_by(protein_start)%>%summarize(netgr_obs_mean=mean(netgr_obs_mean))

il3_dssp=merge(il3,dssp,by="protein_start")
il3_dssp=il3_dssp%>%mutate(exposed=case_when(ACC>=40~"Exposed",
                                            T~"Buried"))
# il3_dssp=il3_dssp%>%filter(exposed%in%"Exposed")
ggplot(il3_dssp,aes(x=ACC))+geom_histogram()



ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+
  cleanup+theme(legend.position = c(.9,.85))+
  theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)+theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v1.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  # facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+cleanup
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v2.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=ACC,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("DSSP Solvent Accessibility at Residue")+
  cleanup+
  labs(color="Solvent \nAccessibility")+
  theme(legend.position = c(.9,.25))+
  theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v3.pdf",width=6,height = 4,units="in",useDingbats=F)



il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%dplyr::select(species,ref_aa,protein_start,alt_aa,netgr_obs_mean)


il3_dssp=merge(il3,dssp,by.x=c("protein_start","ref_aa"),by.y=c("protein_start","AA"))
il3_dssp=il3_dssp%>%mutate(exposed=case_when(ACC>=40~"Exposed",
                                            T~"Buried"))

# il3_dssp=il3_dssp%>%mutate(hydrophobic=case_when(alt_aa%in%c("A","V","I","M","L","F","Y","W")~"hydrophobic",
#                                                  T~"other"))
ggplot(il3_dssp,aes(x=alt_aa,y=netgr_obs_mean))+geom_boxplot()+facet_wrap(~exposed)
ggplot(il3_dssp,aes(x=exposed,y=netgr_obs_mean))+geom_boxplot()+facet_wrap(~exposed)


ggplot(il3_dssp,aes(x=factor(protein_start),y=netgr_obs_mean,fill=exposed))+
  geom_boxplot()+
  # facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_discrete("Residue on the ABL Kinase")+
  labs(fill="Solvent \nAccessibility")+cleanup+
  theme(axis.text.x=element_text(angle=90, hjust=1))

```



Doing some quick analyses on buried hydrophobic vs exposed residues
```{r,eval=F,include=F}
dssp=read.csv("data/DSSP_SolventAccessibility_ABL/2gqg_dspp.csv",header = T)
dssp=dssp%>%mutate(RESIDUE=as.numeric(RESIDUE),ACC=as.numeric(ACC),AA=gsub("<ca>","",AA))
dssp=dssp%>%rename(protein_start=RESIDUE)

il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%select(species,protein_start,netgr_obs_mean)
il3=il3%>%group_by(protein_start)%>%summarize(netgr_obs_mean=mean(netgr_obs_mean))

il3_dssp=merge(il3,dssp,by="protein_start")
il3_dssp=il3_dssp%>%mutate(exposed=case_when(ACC>=40~"Exposed",
                                            T~"Buried"))
ggplot(il3_dssp,aes(x=ACC))+geom_histogram()



ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+
  cleanup+theme(legend.position = c(.9,.85))+
  theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)+theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v1.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  # facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+cleanup
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v2.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=ACC,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("DSSP Solvent Accessibility at Residue")+
  cleanup+
  labs(color="Solvent \nAccessibility")+
  theme(legend.position = c(.9,.25))+
  theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v3.pdf",width=6,height = 4,units="in",useDingbats=F)
```
Doing some quick DDG analysis
```{r}
ddg=read.table("data/DDG_ABL/2hyy_ddg.tsv")
colnames(ddg)=c("species","ddg","ddg_sd")
ddg=ddg%>%mutate(protein_start=234+as.numeric(gsub("[^0-9]","",species)),
                 ref_aa=substr(species,1,1),
                 alt_aa=sub(".+(.)$", "\\1", species),
                 species=paste(ref_aa,protein_start,alt_aa,sep = ""))
# class(ddg$protein_start)
ddg=ddg%>%filter(protein_start%in%c(242:322))

il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%dplyr::select(species,protein_start,netgr_obs_mean)
ddgil3=merge(ddg,il3,by=c("species","protein_start"))
ggplot(ddgil3,aes(x=ddg,y=netgr_obs_mean))+geom_point()
ggplot(ddgil3,aes(x=ddg,y=netgr_obs_mean,label=species))+geom_text()
```

### BaF3 vs K562 correlations. 
  
#### Includes t test to compare distributions of sanger mutants vs resistant mutants

Looking at important sanger mutants across BaF3s and K562s
Includes T tests for sanger boxplots

```{r}
# Analyzing the Sanger data 4.22.2023
sanger=read.csv("data/Cosmic_ABL/ABL_Cosmic_Gene_mutations.csv",header = T)
sanger=sanger%>%dplyr::rename(protein_start=Position,species=AA.Mutation,sanger.count=Count)%>%filter(Type%in%"Substitution - Missense")%>%dplyr::select(protein_start,species,sanger.count)
sanger=sanger%>%mutate(species=gsub("p.","",species),ref_aa=substring(species,1,1),
                       alt_aa=substring(species, nchar(species), nchar(species)))
sanger=sanger%>%mutate(sanger.present=T)
sanger=sanger%>%filter(protein_start%in%242:520)
# sanger=resmuts_adder(sanger)
sum(sanger[sanger$resmuts%in%T,"sanger.count"])
sum(sanger[sanger$resmuts%in%F,"sanger.count"])
# There are a total of 1884 patients with mutations in the kianse. 1193 of these patients have known clinically resistant ImatR mutations. However, 691 of these patients fall into the other category

# K562
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv",header = T,stringsAsFactors = F)
data=data%>%rowwise()%>%mutate(netgr_obs_mean.k562=mean(netgr_obs_screen1,netgr_obs_screen2),netgr_obs_sd.k562=sd(c(netgr_obs_screen1,netgr_obs_screen2)))
data.k562=data%>%dplyr::select(species,protein_start,ref_aa,alt_aa,n_nuc_min,netgr_obs_mean.k562,netgr_obs_sd.k562)
# Baf3
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_medium_rep1vsrep2_ft/screen_comparison_baf3_Imat_medium_rep1vsrep2_ft.csv",header = T,stringsAsFactors = F)
data=data%>%rowwise()%>%mutate(netgr_obs_mean.baf3=mean(netgr_obs_screen1,netgr_obs_screen2),netgr_obs_sd.baf3=sd(c(netgr_obs_screen1,netgr_obs_screen2)))
data.baf3=data%>%dplyr::select(species,protein_start,ref_aa,alt_aa,n_nuc_min,netgr_obs_mean.baf3,netgr_obs_sd.baf3)

data=merge(data.k562,data.baf3,by=c("species","protein_start","ref_aa","alt_aa","n_nuc_min"),all=T)
# data$sanger.present=F
# data$sanger.count=0
data=merge(data,sanger,by=c("species","protein_start","ref_aa","alt_aa"),all=T)

source("code/resmuts_adder.R")
data=resmuts_adder(data)

data=data%>%mutate(cosmic_present=sanger.present)
# data=data%>%mutate(alt_aa=substring(species, nchar(species), nchar(species)))
data$resmut_cosmic="neither"
data[data$cosmic_present%in%TRUE,"resmut_cosmic"]="cosmic"
data[data$resmuts%in%TRUE,"resmut_cosmic"]="resmut"
data$resmut_cosmic=factor(data$resmut_cosmic,levels=c("neither","cosmic","resmut"))


data.forttest=data%>%filter(protein_start>=242,protein_start<=322,n_nuc_min%in%1)
t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.baf3"],
       data.forttest[data.forttest$resmut_cosmic%in%"cosmic","netgr_obs_mean.baf3"])

t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.baf3"],
       data.forttest[data.forttest$resmut_cosmic%in%"resmut","netgr_obs_mean.baf3"])

t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.k562"],
       data.forttest[data.forttest$resmut_cosmic%in%"cosmic","netgr_obs_mean.k562"])

t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.k562"],
       data.forttest[data.forttest$resmut_cosmic%in%"resmut","netgr_obs_mean.k562"])


ggplot(data%>%filter(sanger.present%in%T,n_nuc_min%in%1),aes(x=netgr_obs_mean.baf3,y=netgr_obs_mean.k562))+
  geom_point()+
  stat_cor(method="pearson")

ggplot(data%>%filter(sanger.present%in%T,n_nuc_min%in%1),aes(x=netgr_obs_mean.baf3,y=netgr_obs_mean.k562,label=species,color=resmuts))+
  geom_text(size=1.6)+
  # stat_cor(method="pearson")+
  cleanup+
  scale_x_continuous("Net Growth Rate Baf3")+
  scale_y_continuous("Net Growth Rate K562")+
  scale_color_manual(values=c("orange","red"))+
  theme(legend.position = "none")
# ggsave("output/SM_Imatinib_Plots/baf3_k562_sanger_correlation.pdf",width=3,height=3,units = "in",useDingbats=F)



```


### BaF3 K562s ROC curves
  
Doing ROC analyses between BaF3s and K562s
```{r}
smdata.k562=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_high_rep1vsrep2/screen_comparison_k562_imat_high_rep1vsrep2.csv")
# smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_low_rep1vsrep2/screen_comparison_k562_imat_low_rep1vsrep2.csv")
# smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv")
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_low_rep1vsrep2_ft/screen_comparison_baf3_imat_low_rep1vsrep2_ft.csv")
# smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_medium_rep1vsrep2_ft/screen_comparison_baf3_imat_medium_rep1vsrep2_ft.csv")
smdata.baf3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_high_rep1vsrep2_ft/screen_comparison_baf3_imat_high_rep1vsrep2_ft.csv")
smdata.baf3=cosmic_data_adder(smdata.baf3)
smdata.k562=cosmic_data_adder(smdata.k562)

smdata.baf3=smdata%>%filter(!species%in%"V299L")
smdata.baf3=smdata.baf3%>%filter(n_nuc_min%in%1)
smdata.k562=smdata.k562%>%filter(n_nuc_min%in%1)

smdata.baf3=smdata.baf3%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
smdata.baf3=smdata.baf3%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
# Demonstrating that the SM data works better at predicting residue exposure than the BE data
# smdata_roc=smdata%

# glm.fit.sm=glm(as.numeric(smdata$cosmic_present)~smdata$netgr_obs_mean,family=binomial)

glm.fit.baf3=glm(as.numeric(smdata.baf3$resmuts)~smdata.baf3$netgr_obs_mean,family=binomial)
glm.fit.k562=glm(as.numeric(smdata.k562$resmuts)~smdata.k562$netgr_obs_mean,family=binomial)
smdata.baf3$glm_fits=glm.fit.baf3$fitted.values
smdata.k562$glm_fits=glm.fit.k562$fitted.values
# roc(as.numeric(smdata$cosmic_present),smdata$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True
#     Positive Percentage",print.auc=T)
roc(as.numeric(smdata.baf3$resmuts),smdata.baf3$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T)
roc(as.numeric(smdata.k562$resmuts),smdata.k562$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T)
# The GLM in this case looks a little weird, probably because there are so many negative datapoints
# ggplot(smdata.baf3,aes(x=netgr_obs_mean,y=as.numeric(resmuts)))+geom_point()+geom_line(aes(x=netgr_obs_mean,y=glm_fits))
# ggplot(smdata.k562,aes(x=netgr_obs_mean,y=as.numeric(resmuts)))+geom_point()+geom_line(aes(x=netgr_obs_mean,y=glm_fits))

par(pty="s")
roc(as.numeric(smdata.baf3$resmuts),smdata.baf3$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T,col="#3937E3",lwd=4)

# plot.roc(as.numeric(be_lfc.sm$DSSP.Buried),be_lfc.sm$glm_fits,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T,col="#378BE3",add=T,lwd=4,print.auc.y=45)
plot.roc(as.numeric(smdata.k562$resmuts),smdata.k562$glm_fits,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T,col="#378BE3",add=T,lwd=4,print.auc.y=45)
par(pty="m")
```


### VUDR Pie Chart, clinical abundance waterfall
   
Making piechart that shows that VUDR take up 36%
```{r}
# 
sanger_forpiechart=resmuts_adder(sanger)
sanger_forpiechart$category="VUDR"
sanger_forpiechart=sanger_forpiechart%>%mutate(category=case_when(resmuts%in%T~species,
                                                                  T~category))



sanger_forpiechart=sanger_forpiechart%>%group_by(category)%>%summarize(count=sum(sanger.count))
sanger_forpiechart=sanger_forpiechart%>%arrange(desc(count))
sanger_forpiechart$category=factor(sanger_forpiechart$category,levels = as.character(sanger_forpiechart$category[order((sanger_forpiechart$count),decreasing = T)]))

#Plotting the normalized dose response curves
getPalette = colorRampPalette(brewer.pal(22, "Spectral"))

library(RColorBrewer)
library("NatParksPalettes")
ggplot(sanger_forpiechart,aes(x="",y=count,fill=category))+
  geom_bar(width=1,stat="identity")+
  coord_polar("y", start=0)+
  # theme_minimal()+
  theme_void()+
  # scale_fill_manual(values=natparks.pals("Yellowstone", 3))
  scale_fill_manual(values = getPalette(length(unique(sanger_forpiechart$category))))
# ggsave("output/SM_Imatinib_Plots/sanger_piechart.pdf",width=4,height=3,units="in",useDingbats=F)

```


Making histogram of top clinically prevalent sanger mutants
```{r}
library(forcats)
# Analyzing the Sanger data 4.22.2023
sanger=read.csv("data/Cosmic_ABL/ABL_Cosmic_Gene_mutations.csv",header = T)
sanger=sanger%>%dplyr::rename(protein_start=Position,species=AA.Mutation,sanger.count=Count)%>%filter(Type%in%"Substitution - Missense")%>%dplyr::select(protein_start,species,sanger.count)
sanger=sanger%>%mutate(species=gsub("p.","",species),ref_aa=substring(species,1,1),
                       alt_aa=substring(species, nchar(species), nchar(species)))
sanger=sanger%>%mutate(sanger.present=T)

sanger=sanger%>%group_by(species)%>%summarize(protein_start=mean(protein_start),sanger.count=sum(sanger.count))
sanger$resmuts=F
sanger[sanger$species%in%c("E355A","D276G","H396R","F317L","F359I","E459K","G250E","F359C","F359V","M351T","L248V","E355G","Q252H","Y253F","F486S","H396P","E255K","Y253H","T315I","E255V","M244V","V299L","L387M"),"resmuts"]=T


ggplot(sanger%>%filter(resmuts%in%T),aes(fct_reorder(species, -sanger.count),y=sanger.count,fill=resmuts))+
  geom_col(color="black",alpha=0.8)+
  scale_x_discrete("Mutant Name")+
  scale_y_continuous("Clinical Abundance")+
  scale_fill_manual(values=c("red"))+
  cleanup+
  theme(legend.position = "none",
        axis.text.x=element_text(angle=90,hjust=.5,vjust=.5),
        axis.title.x=element_blank())
# ggsave("output/SM_Imatinib_Plots/clinical_abundance_zoom.pdf",width=5,height=3,units="in",useDingbats=F)

ggplot(sanger,aes(fct_reorder(species, -sanger.count),y=sanger.count,fill=resmuts))+
  geom_col(alpha=0.8)+
  scale_x_discrete("Mutant Name")+
  scale_y_continuous("Clinical Abundance")+
  scale_fill_manual(values=c("gray90","red"))+
  # cleanup+
  theme(legend.position = "none",
        axis.text.x=element_text(size=2,angle=90,hjust=.5,vjust=.5),
        axis.title.x=element_blank())
# ggsave("output/SM_Imatinib_Plots/clinical_abundance.pdf",width=14,height=3,units="in",useDingbats=F)

ggplot(sanger,aes(fct_reorder(species, -sanger.count),y=sanger.count,fill=resmuts))+
  geom_col()+
  scale_x_discrete("Mutant Name")+
  scale_y_continuous("Clinical Abundance")+
  scale_fill_manual(values=c("gray90","red"))+
  theme(legend.position = "none",
        axis.text.x=element_text(angle=90,hjust=.5,vjust=.5),
        axis.title.x=element_blank())

```

### SSCS vs NGS on region 1 data

Doing quick correlation of lane 18b sample 4 NGS vs SSCS
```{r}
ngs=read.csv("data/Consensus_Data/novogene_lane18/sample4/ngs/variant_caller_outputs/variants_unique_ann.csv")
ngs=ngs%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf)
sscs=read.csv("data/Consensus_Data/novogene_lane18/sample4/sscs/variant_caller_outputs/variants_unique_ann.csv")
sscs=sscs%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf)

ngs_sscs=merge(ngs,sscs,by=c("ref_aa","protein_start","alt_aa","alt_codon"))
ngs_sscs=ngs_sscs%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep=""))
# ngs_sscs=ngs_sscs%>%filter(alt_codon%in%twist_alt_codon)

# plotly=ggplot(ngs_sscs,aes(x=maf.x,y=maf.y))+geom_point()+scale_x_continuous("NGS",trans="log10")+scale_y_continuous("SSCS",trans="log10")
# ggplotly(plotly)

plotly=ggplot(ngs_sscs,aes(x=maf.x,y=maf.y,label=species))+geom_text()+scale_x_continuous("NGS",trans="log10")+scale_y_continuous("SSCS",trans="log10")+geom_abline()
ggplotly(plotly)

plotly=ggplot(ngs_sscs,aes(x=maf.x,y=maf.y,label=species))+geom_text()+scale_x_continuous("NGS")+scale_y_continuous("SSCS")+geom_abline()
ggplotly(plotly)

x=ngs%>%filter(protein_start%in%255,alt_aa%in%"L",alt_codon%in%"CTG")
x=ngs_sscs%>%filter(species%in%"E255L")
codon_table=read.csv("data/codon_table.csv",header = T,stringsAsFactors = F)

  twist_codons=codon_table%>%filter(Twist%in%T)
  # twist_alt_codon=twist_codons[twist_codons$Letter%in%alt_aa,"Codon"]
twist_alt_codon=twist_codons[,"Codon"]
```

```{r}

sample10=read.csv("data/Consensus_Data/novogene_lane18/sample10/ngs/variant_caller_outputs/variants_unique_ann.csv")
# sample10=sample10%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf.d0=maf)
sample10=sample10%>%
  # filter(protein_start%in%c(242:272))%>%
  filter(protein_start%in%c(242:322))%>%
  mutate(maf=ct/depth,
         species=paste(ref_aa,protein_start,alt_aa,sep=""))%>%
  dplyr::select(type,ref_aa,protein_start,alt_aa,alt_codon,species,maf.d0=maf)
sample10=sample10%>%filter(alt_codon%in%twist_alt_codon)%>%
  group_by(type,ref_aa,protein_start,alt_aa,alt_codon,species)%>%
  summarize(maf.d0=max(maf.d0))

sample4=read.csv("data/Consensus_Data/novogene_lane18/sample4/ngs/variant_caller_outputs/variants_unique_ann.csv")
sample4=sample4%>%
  # filter(protein_start%in%c(242:272))%>%
  filter(protein_start%in%c(242:322))%>%
  mutate(maf=ct/depth,
         species=paste(ref_aa,protein_start,alt_aa,sep=""))%>%
  dplyr::select(type,ref_aa,protein_start,alt_aa,alt_codon,species,maf.screen1=maf)
sample4=sample4%>%filter(alt_codon%in%twist_alt_codon)%>%
  group_by(type,ref_aa,protein_start,alt_aa,alt_codon,species)%>%
  summarize(maf.screen1=max(maf.screen1))


sample5=read.csv("data/Consensus_Data/novogene_lane18/sample5/ngs/variant_caller_outputs/variants_unique_ann.csv")
sample5=sample5%>%
  # filter(protein_start%in%c(242:272))%>%
  filter(protein_start%in%c(242:322))%>%
  mutate(maf=ct/depth,
         species=paste(ref_aa,protein_start,alt_aa,sep=""))%>%
  dplyr::select(type,ref_aa,protein_start,alt_aa,alt_codon,species,maf.screen2=maf)
sample5=sample5%>%filter(alt_codon%in%twist_alt_codon)%>%
  group_by(type,ref_aa,protein_start,alt_aa,alt_codon,species)%>%
  summarize(maf.screen2=max(maf.screen2))


# sample5=sample5%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf.screen2=maf)

baf3_low=merge(sample10,sample4,by=c("type","ref_aa","protein_start","alt_aa","alt_codon"))
baf3_low=merge(baf3_low,sample5,by=c("type","ref_aa","protein_start","alt_aa","alt_codon"))
# baf3_low=baf3_low%>%filter(alt_codon%in%twist_alt_codon)
baf3_low=baf3_low%>%mutate(netgr_screen1=log(maf.screen1*25546/(maf.d0*54))/144,
                           netgr_screen2=log(maf.screen2*22471/(maf.d0*54))/144)

plotly=ggplot(baf3_low,aes(x=netgr_screen1,y=netgr_screen2))+geom_point()+scale_x_continuous(trans="log10")+scale_y_continuous(trans="log10")+facet_wrap(~type)
ggplotly(plotly)
source("code/resmuts_adder.R")
baf3_low=resmuts_adder(baf3_low)
plotly=ggplot(baf3_low,aes(x=netgr_screen1,y=netgr_screen2,label=species,color=resmuts))+geom_text()+scale_x_continuous(trans="log10")+scale_y_continuous(trans="log10")
ggplotly(plotly)
cor(baf3_low$netgr_screen1,baf3_low$netgr_screen2)

class(baf3_low$netgr_screen1)
baf3_low=baf3_low%>%mutate(netgr_obs_mean=(netgr_screen1+netgr_screen2)/2)

glm.fit.baf3=glm(as.numeric(baf3_low$resmuts)~baf3_low$netgr_obs_mean,family=binomial)
baf3_low$glm_fits=glm.fit.baf3$fitted.values
roc(as.numeric(baf3_low$resmuts),baf3_low$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T)

baf3_low2=baf3_low%>%filter(!protein_start%in%c(289:306))%>%dplyr::select(ref_aa,protein_start,alt_aa,species,netgr_obs_mean)
# baf3_low=
  
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_low_rep1vsrep2_ft/screen_comparison_baf3_imat_low_rep1vsrep2_ft.csv")
smdata=smdata%>%filter(!ct_screen1_after%in%.5,!ct_screen1_after%in%.5)
smdata=smdata%>%filter(!protein_start%in%c(289:306))%>%dplyr::select(ref_aa,protein_start,alt_aa,species,netgr_obs_mean)

  
baf3_low2=merge(baf3_low2,smdata,by=c("ref_aa","protein_start","alt_aa","species"),all = T)
baf3_low2=baf3_low2%>%filter(!ref_aa==alt_aa)
baf3_low2$ngsonly=F
baf3_low2[baf3_low2$netgr_obs_mean.y%in%NA,"ngsonly"]=T
baf3_low2[baf3_low2$netgr_obs_mean.y%in%NA,"netgr_obs_mean.y"]=.01
  
ggplot(baf3_low2,aes(x=netgr_obs_mean.x,y=netgr_obs_mean.y,label=species,color=ngsonly))+geom_text()+stat_cor(method = "pearson")
x=baf3_low2%>%filter(netgr_obs_mean.y%in%NA)

smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_low_rep1vsrep2_ft/screen_comparison_baf3_imat_low_rep1vsrep2_ft.csv")
ggplot(smdata,aes(x=ct_screen1_after,y=netgr_obs_mean))+geom_point()+scale_x_continuous(trans="log10")
```
