---
title: "ABL_sheared_libraries"
author: "Haider Inam"
date: '2023-01-31'
output: html_document
---
This code has some of the analysis done for libraries made using the enzymatic fragrmentation library prep approach (mostly data from lane 11-16)

These are sheared TSII +TSI libraries treated at 300nM imatinib for 2 or 4 or 6 days
URL for experiments: https://benchling.com/haider-inam/f/lib_4VmxpyTI-archive/etr_msCPLyuR-twist-sorted-pooled-screen-tsi-1/edit
Note: A small part of the data from these sheared libraries was eventually used in the final ABL dataset! 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath(".."))

library(stringr)
library(dplyr)
library(ggplot2)
library(plotly)
library(tictoc)
library(doParallel)
library(foreach)
library(RColorBrewer)
#Cleanup code for plotting
# cleanup=theme_bw() +
#   theme(plot.title = element_text(hjust=.5), 
#         panel.grid.major = element_blank(),
#         panel.grid.major.y = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(color = "black"),
#         axis.text = element_text(face="bold",color="black",size="11"),
#         text=element_text(size=11,face="bold"),
#         axis.title=element_text(face="bold",size="11"))

```

```{r}
source("code/merge_samples.R")
source("code/variants_parser.R")
source("code/shortest_codon_finder.R")
source("code/compare_samples.R")
source("code/depth_finder.R")
source("code/resmuts_adder.R")
source("code/res_residues_adder.R")
source("code/plotting/cleanup.R")

```

For the density plots:
```{r}
library(viridisLite)
library("MASS")

theme_set(theme_bw(base_size = 16))

# Get density of points in 2 dimensions.
# @param x A numeric vector.
# @param y A numeric vector.
# @param n Create a square n by n grid to compute density.
# @return The density within each square.
get_density <- function(x, y, ...) {
  dens <- MASS::kde2d(x, y, ...)
  ix <- findInterval(x, dens$x)
  iy <- findInterval(y, dens$y)
  ii <- cbind(ix, iy)
  return(dens$z[ii])
}

set.seed(1)
dat <- data.frame(
  x = c(
    rnorm(1e4, mean = 0, sd = 0.1),
    rnorm(1e3, mean = 0, sd = 0.1)
  ),
  y = c(
    rnorm(1e4, mean = 0, sd = 0.1),
    rnorm(1e3, mean = 0.1, sd = 0.2)
  )
)
```

Function to find the shortest possible ALT codon for a given amino acid substitution


```{r}
TP3D6=read.csv("data/Consensus_Data/novogene_lane17/sample6/sscs/variant_caller_outputs/variants_unique_ann.csv",header = T,stringsAsFactors = F)
TP3D6=variants_parser(TP3D6,93000)

TP3D2=read.csv("data/Consensus_Data/novogene_lane17/sample7/sscs/variant_caller_outputs/variants_unique_ann.csv",header = T,stringsAsFactors = F)
TP3D2=variants_parser(TP3D2,839)

TP3D2.D6=compare_samples(TP3D2,TP3D6,.055,96)

# TP3D2.D6=TP3D2.D6%>%filter(ct.x>=3)

TP3D2.D6_clinrel=TP3D2.D6%>%filter(n_nuc_min==1)

TP3D2.D6_clinrel=resmuts_adder(TP3D2.D6_clinrel)
TP3D2.D6_clinrel=res_residues_adder(TP3D2.D6_clinrel)

resmuts=TP3D2.D6_clinrel%>%filter(resmuts%in%T)%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))

ic50data_all_sum=read.csv("output/ic50data_all_confidence_intervals_raw_data.csv",row.names = 1)
resmuts_merged=merge(resmuts,ic50data_all_sum,by="species")

ggplot(resmuts_merged,aes(x=netgr_pred_model,y=netgr_obs,label=species))+geom_text()+geom_abline()

ggplot(resmuts_merged,aes(x=netgr_pred_model,y=score,label=species))+geom_text()+geom_abline()


```


```{r}
il3D0=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
il3D0=merge_samples_twosamples(il3D0,"Novogene_lane14/sample11/sscs")
il3D0=merge_samples_twosamples(il3D0,"Novogene_lane15/sample_3/sscs")
# il3D0=merge_samples(il3D0,"Novogene_lane17/sample1_combined/sscs")

il3D0=variants_parser(il3D0,370)

imatD4=read.csv("data/Consensus_Data/novogene_lane15/sample_7/sscs/variant_caller_outputs/variants_unique_ann.csv",header = T,stringsAsFactors = F)

imatD4=variants_parser(imatD4,10000)

TSIID0.D4=compare_samples(il3D0,imatD4,.055,96)

# TSIID0.D4=TSIID0.D4%>%filter(ct.x>=3)

TSIID0.D4_clinrel=TSIID0.D4%>%filter(n_nuc_min==1)

TSIID0.D4_clinrel=resmuts_adder(TSIID0.D4_clinrel)
TSIID0.D4_clinrel=res_residues_adder(TSIID0.D4_clinrel)

resmuts=TSIID0.D4_clinrel%>%filter(resmuts%in%T)%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))

ic50data_all_sum=read.csv("output/ic50data_all_confidence_intervals_raw_data.csv",row.names = 1)
resmuts_merged=merge(resmuts,ic50data_all_sum,by="species")

ggplot(resmuts_merged,aes(x=netgr_pred_model,y=netgr_obs,label=species))+geom_text()+geom_abline()

ggplot(resmuts_merged%>%filter(!species%in%(c("T315I","F317L"))),aes(x=netgr_pred_model,y=netgr_obs,label=species))+geom_text()+geom_abline()
```



```{r}
TSIID0.D4_clinrel_simple=TSIID0.D4_clinrel%>%dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))

TP3D2.D6_clinrel_simple=TP3D2.D6_clinrel%>%dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))

screen_compare=merge(TSIID0.D4_clinrel_simple,
                     TP3D2.D6_clinrel_simple,
                     by=c("ref_aa","protein_start","alt_aa","ref","alt","alt_start_pos","consequence_terms","ref_codon","alt_codon","alt_codon_shortest","n_nuc_min"),
                     all.x=T,
                     all.y=T)

screen_compare=resmuts_adder(screen_compare)
screen_compare=screen_compare%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))

plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,label=species,color=resmuts))+geom_text()+geom_abline()
ggplotly(plotly)

plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,color=resmuts))+geom_point()+geom_abline()
ggplotly(plotly)
# Side note: check how many of the top mutations are good by cosmic
# Check TP4 vs TP3 agreement. Check 

# Next, I'm going to calculate the weighted mean of the scores across the concomitant vs in series screens
screen_compare_means=screen_compare%>%
  filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)%>%
  rowwise()%>%
  mutate(score_mean=mean(c(score.x,score.y)))

a=screen_compare%>%
  filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)
```


TSID0.D2
TSID0.D4
TSID0.D6
Comparisons:
D0.D2 vs D2 D4 vs D4 D6

Day 0 Day 2 vs Day 0 Day 4
```{r}
###### TSI Day 0 vs Day 2 #########
delta_t=48 #hours
cells_before=107 #total cells at before time point
cells_after=1515 #total cells at after time point
netgr=.055

# before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane14/sample11/sscs")

before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
before_timepoint=merge_samples_twosamples(before_timepoint,"Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples_twosamples(before_timepoint,"Novogene_lane15/sample_3/sscs")

# before_timepoint=merge_samples("Novogene_lane15/sample_3/sscs","Novogene_lane13/sample7/sscs")

before_timepoint=variants_parser(before_timepoint,cells_before)
after_timepoint=merge_samples("Novogene_lane13/Sample9/sscs","Novogene_lane13/Sample10/sscs")
after_timepoint=merge_samples_twosamples(after_timepoint,"Novogene_lane15/Sample_4/sscs")

after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

before_after=before_after%>%filter(ct.x>=3)
before_after_screen1=before_after


###### TSI Day 0 vs Day 4 #########
delta_t=96 #hours
cells_before=107 #total cells at before time point
cells_after=17239 #total cells at after time point
netgr=.055
# before_timepoint=merge_samples("Novogene_lane15/sample_3/sscs","Novogene_lane13/sample7/sscs")

before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
before_timepoint=merge_samples_twosamples(before_timepoint,"Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples_twosamples(before_timepoint,"Novogene_lane15/sample_3/sscs")



before_timepoint=variants_parser(before_timepoint,cells_before)

after_timepoint=read.csv("data/Consensus_Data/novogene_lane15/sample_5/sscs/variant_caller_outputs/variants_unique_ann.csv")

after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

before_after=before_after%>%filter(ct.x>=3)
before_after_screen2=before_after


before_after_screen1=before_after_screen1%>%
  mutate(ct_screen1=ct.x)%>%
  dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))


before_after_screen2=before_after_screen2%>%
  mutate(ct_screen2=ct.x)%>%
  dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))

screen_compare=merge(before_after_screen1,
                     before_after_screen2,
                     by=c("ref_aa","protein_start","alt_aa","ref","alt","alt_start_pos","consequence_terms","ref_codon","alt_codon","alt_codon_shortest","n_nuc_min"),
                     all.x=T,
                     all.y=T)

screen_compare=resmuts_adder(screen_compare)
screen_compare=res_residues_adder(screen_compare)
screen_compare=screen_compare%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))


############### Adding Count, Depth, and MAF columns for Ivan 2.20.23###########
# a=before_after_screen1
# b=before_after_screen2
# before_after_screen1=a
# before_after_screen2=b

# before_after_screen1=before_after_screen1%>%
#   mutate(ct_screen1_before=ct.x,
#          depth_screen1_before=depth.x,
#          maf_screen1_before=maf.x,
#          ct_screen1_after=ct.y,
#          depth_screen1_after=depth.y,
#          maf_screen1_after=maf.y)%>%
#   dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))
# 
# before_after_screen2=before_after_screen2%>%
#   mutate(ct_screen2_before=ct.x,
#          depth_screen2_before=depth.x,
#          maf_screen2_before=maf.x,
#          ct_screen2_after=ct.y,
#          depth_screen2_after=depth.y,
#          maf_screen2_after=maf.y)%>%
#   dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))
# 
# screen_compare=merge(before_after_screen1,
#                      before_after_screen2,
#                      by=c("ref_aa","protein_start","alt_aa","ref","alt","alt_start_pos","consequence_terms","ref_codon","alt_codon","alt_codon_shortest","n_nuc_min"),
#                      all.x=T,
#                      all.y=T,suffixes = c("_screen1","_screen2"))
# 
# screen_compare=resmuts_adder(screen_compare)
# screen_compare=res_residues_adder(screen_compare)
# screen_compare=screen_compare%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))
# 
# screen_compare_means=screen_compare%>%
#   filter(!score_screen1%in%NA,!score_screen2%in%NA,!score_screen1%in%NaN,!score_screen2%in%NaN)%>%
#   rowwise()%>%
#   mutate(score_mean=mean(c(score_screen1,score_screen2)))

# write.csv(screen_compare_means,"IL3_Enrichment_bgmerged_2.20.23.csv")

##############
plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,label=species,color=resmuts))+geom_text()+geom_abline()
ggplotly(plotly)

plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,color=resmuts))+geom_point()+geom_abline()
ggplotly(plotly)
a=screen_compare%>%filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)
cor(a$score.x,a$score.y)

screen_compare_means=screen_compare%>%
  filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)%>%
  rowwise()%>%
  mutate(score_mean=mean(c(score.x,score.y)),
         score_weighteed_mean=weighted.mean(c(score.x,score.y),c(ct_screen1,ct_screen2)))

# write.csv(screen_compare_means,"IL3_Enrichment_2.12.23.csv")

ggplot(screen_compare%>%filter(protein_start>=242,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=score.x))+geom_tile()


screen_compare=screen_compare%>%filter(!score.x%in%c(NA,NaN),!score.y%in%c(NA,NaN))
screen_compare$density=get_density(x = screen_compare$score.x,y=screen_compare$score.y,n=100)
ggplot(screen_compare,aes(x=score.x,y=score.y,color=density))+
  geom_point()+
  scale_color_viridis_c()+
  # geom_jitter(position = position_jitter(width = 0.2, height = 0.2))+
  # scale_x_continuous(name="Score Replicate 1",limits=c(-4,4))+
  # scale_y_continuous(name="Score Replicate 2",limits=c(-4,4))+
  geom_abline(linetype="dashed")+
  theme(legend.position = "none")
# ggsave("il3d0d2.d0d4_score_2.15.23.pdf",width=6,height=6,units="in",useDingbats=F)


a=screen_compare%>%filter(!score.x%in%c(NA,NaN),!score.y%in%c(NA,NaN))
cor(a$score.x,a$score.y)

# screen_compare$resmuts=factor(screen_compare$resmuts,levels=c("TRUE","FALSE"))
ggplot(screen_compare,aes(x=score.x,y=score.y))+
  geom_point(color="black",shape=21,aes(fill=resmuts))+
  geom_abline()+
  scale_x_continuous(name="Score D0 D2")+
  scale_y_continuous(name="Score D0 D4")+
  labs(fill="Resistant\n Mutant")+
  scale_fill_manual(values=c("gray90","red"))

ggplot(screen_compare,aes(x=score.x,y=score.y))+
  geom_point()+
  geom_abline()+
  scale_x_continuous(name="Score D0 D2")+
  scale_y_continuous(name="Score D0 D4")+
  labs(fill="Resistant\n Mutant")
# ggsave("il3d0d2.d0d4_score_2.15.23.pdf",width=8,height=6,units="in",useDingbats=F)

data=read.csv("IL3_Enrichment_2.12.23.csv",header = T,stringsAsFactors = F)
data=data%>%filter(ct_screen1>=3,ct_screen2>=3)


```

```{r}
screen_compare[screen_compare$score.x%in%NA,"score.x"]=-6

#####Graying out unseen residues#####
df_grid  = expand.grid(protein_start = c(242:493),alt_aa = unique(screen_compare$alt_aa))

###Trying to add in the score as WT for residues that are wt
reference_seq=read.table("data/Refs/ABL/abl_cds_translation.txt")
screen_compare=screen_compare%>%
  rowwise()%>%
  # group_by(protein_start)%>%
  mutate(ref_aa=case_when(ref_aa%in%NA~substr(reference_seq,protein_start,protein_start),
                          T~ref_aa))%>%
  mutate(wt=case_when(ref_aa==alt_aa~T,
                      T~F))

##########Plotting gray and yellow heatmap
# screen_compare=screen_compare%>%mutate(score.x)

screen_compare$alt_aa=factor(screen_compare$alt_aa,levels=c("P","G","Y","W","F","V","L","I","A","T","S","Q","N","M","C","E","D","R","K","H"))
screen_compare.filtered=screen_compare%>%filter(!protein_start%in%c(290:305))
# a=il3D0.D4.merge.filtered%>%filter(wt%in%T)
ggplot(screen_compare.filtered,aes(x=protein_start,y=alt_aa))+
  geom_tile(data=subset(screen_compare.filtered,!is.na(score.x)),aes(fill=score.x))+
  scale_fill_gradient2(low ="darkblue",midpoint=.03,mid="white", high ="red",name="Score")+
  geom_tile(data=subset(screen_compare.filtered,is.na(score.x)&wt%in%F),aes(color="white"),linetype = "solid",color="white", fill = "gray90", alpha = 0.8)+
  geom_tile(data=subset(screen_compare.filtered,is.na(score.x)&wt%in%T),aes(color="white"),linetype = "solid",color="white", fill = "yellow", alpha = 0.4)+
  theme(panel.background=element_rect(fill="white", colour="black"))+scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,493),expand=c(0,0))+
  ylab("Mutant Amino Acid")
# ggsave("BCRABL_IL3_D0D4_2.12.23.pdf",height=6,width=24,units="in",useDingbats=F)


ggplot(screen_compare.filtered,aes(x=score.x,y=score.y))+geom_point()
```



IL3 Day 0 Day 4 vs Day 2 Day 6
```{r}
###### TSI Day 0 vs Day 4 #########
delta_t=96 #hours
cells_before=107 #total cells at before time point
cells_after=17239 #total cells at after time point
netgr=.055

before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane15/sample_3/sscs")

before_timepoint=variants_parser(before_timepoint,cells_before)

after_timepoint=read.csv("data/Consensus_Data/novogene_lane15/sample_5/sscs/variant_caller_outputs/variants_unique_ann.csv")



after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

# before_after=before_after%>%filter(ct.x>=3)
before_after_screen1=before_after


###### TSI Day 2 vs Day 6 #########
delta_t=96 #hours
cells_before=1515 #total cells at before time point
cells_after=430713 #total cells at after time point
netgr=.055
before_timepoint=merge_samples("Novogene_lane13/Sample9/sscs","Novogene_lane13/Sample10/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane15/Sample_4/sscs")

before_timepoint=variants_parser(before_timepoint,cells_before)

after_timepoint=read.csv("data/Consensus_Data/novogene_lane17/sample2/sscs/variant_caller_outputs/variants_unique_ann.csv")

after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

# before_after=before_after%>%filter(ct.x>=3)
before_after_screen2=before_after


before_after_screen1=before_after_screen1%>%
  mutate(ct_screen1=ct.x)%>%
  dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))


before_after_screen2=before_after_screen2%>%
  mutate(ct_screen2=ct.x)%>%
  dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))

screen_compare=merge(before_after_screen1,
                     before_after_screen2,
                     by=c("ref_aa","protein_start","alt_aa","ref","alt","alt_start_pos","consequence_terms","ref_codon","alt_codon","alt_codon_shortest","n_nuc_min"),
                     all.x=T,
                     all.y=T)

screen_compare=resmuts_adder(screen_compare)
screen_compare=screen_compare%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))

plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,label=species,color=resmuts))+geom_text()+geom_abline()
ggplotly(plotly)

plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,color=resmuts))+geom_point()+geom_abline()
ggplotly(plotly)

screen_compare_means=screen_compare%>%
  filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)%>%
  rowwise()%>%
  mutate(score_mean=mean(c(score.x,score.y)),
         score_weighteed_mean=weighted.mean(c(score.x,score.y),c(ct_screen1,ct_screen2)))

# write.csv(screen_compare_means,"IL3_Enrichment_2.8.23.csv")

ggplot(screen_compare%>%filter(protein_start>=242,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=score.x))+geom_tile()

a=screen_compare%>%filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)
cor(a$score.x,a$score.y)
```

```{r}
screen_compare[screen_compare$score.x%in%NA,"score.x"]=-6

#####Graying out unseen residues#####
df_grid  = expand.grid(protein_start = c(242:493),alt_aa = unique(screen_compare$alt_aa))

###Trying to add in the score as WT for residues that are wt
reference_seq=read.table("data/Refs/ABL/abl_cds_translation.txt")
screen_compare=screen_compare%>%
  rowwise()%>%
  # group_by(protein_start)%>%
  mutate(ref_aa=case_when(ref_aa%in%NA~substr(reference_seq,protein_start,protein_start),
                          T~ref_aa))%>%
  mutate(wt=case_when(ref_aa==alt_aa~T,
                      T~F))

##########Plotting gray and yellow heatmap
# screen_compare=screen_compare%>%mutate(score.x)

screen_compare$alt_aa=factor(screen_compare$alt_aa,levels=c("P","G","Y","W","F","V","L","I","A","T","S","Q","N","M","C","E","D","R","K","H"))
screen_compare.filtered=screen_compare%>%filter(!protein_start%in%c(290:305))
# a=il3D0.D4.merge.filtered%>%filter(wt%in%T)
ggplot(screen_compare.filtered,aes(x=protein_start,y=alt_aa))+
  geom_tile(data=subset(screen_compare.filtered,!is.na(score.x)),aes(fill=score.x))+
  scale_fill_gradient2(low ="darkblue",midpoint=.03,mid="white", high ="red",name="Score")+
  geom_tile(data=subset(screen_compare.filtered,is.na(score.x)&wt%in%F),aes(color="white"),linetype = "solid",color="white", fill = "gray90", alpha = 0.8)+
  geom_tile(data=subset(screen_compare.filtered,is.na(score.x)&wt%in%T),aes(color="white"),linetype = "solid",color="white", fill = "yellow", alpha = 0.4)+
  theme(panel.background=element_rect(fill="white", colour="black"))+scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,493),expand=c(0,0))+
  ylab("Mutant Amino Acid")
# ggsave("BCRABL_IL3_D0D4_2.8.23.pdf",height=6,width=24,units="in",useDingbats=F)


ggplot(screen_compare.filtered,aes(x=score.x,y=score.y))+geom_point()
```




Imatinib Screens
Day 0 Day 2 vs Day 0 Day 4
```{r}
###### TSII Day 0 vs Day 2 #########

delta_t=48 #hours
cells_before=370 #total cells at before time point
cells_after=1192.25 #total cells at after time point
netgr=.055
# before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane15/sample_3/sscs")
# source()
before_timepoint=variants_parser(before_timepoint,cells_before)

after_timepoint=merge_samples("Novogene_lane15/sample_6/sscs","Novogene_lane14/sample12/sscs")
# after_timepoint=merge_samples(after_timepoint,"Novogene_lane15/Sample_4/sscs")
# after_timepoint=read.csv("data/Consensus_Data/novogene_lane15/sample_7/sscs/variant_caller_outputs/variants_unique_ann.csv")

after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

before_after=before_after%>%filter(ct.x>=3)
before_after_screen1=before_after


###### TSII Day 0 vs Day 4 #########
delta_t=96 #hours
cells_before=370 #total cells at before time point
cells_after=10397 #total cells at after time point
netgr=.055
# before_timepoint=merge_samples("Novogene_lane15/sample_3/sscs","Novogene_lane13/sample7/sscs")
source("code/merge_samples_twosamples.R")
before_timepoint=merge_samples_twosamples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
before_timepoint=merge_samples_twosamples(before_timepoint,"Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples_twosamples(before_timepoint,"Novogene_lane15/sample_3/sscs")



before_timepoint=variants_parser(before_timepoint,cells_before)

after_timepoint=read.csv("data/Consensus_Data/novogene_lane15/sample_7/sscs/variant_caller_outputs/variants_unique_ann.csv")
# after_timepoint=read.csv("data/Consensus_Data/novogene_lane17/sample3/sscs/variant_caller_outputs/variants_unique_ann.csv")

after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

# before_after=before_after%>%filter(ct.x>=3)
before_after_screen2=before_after



############### Adding Count, Depth, and MAF columns for Ivan 2.20.23###########
# a=before_after_screen1
# b=before_after_screen2
# before_after_screen1=a
# before_after_screen2=b

# before_after_screen1=before_after_screen1%>%
#   mutate(ct_screen1_before=ct.x,
#          depth_screen1_before=depth.x,
#          maf_screen1_before=maf.x,
#          ct_screen1_after=ct.y,
#          depth_screen1_after=depth.y,
#          maf_screen1_after=maf.y)%>%
#   dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))
# 
# before_after_screen2=before_after_screen2%>%
#   mutate(ct_screen2_before=ct.x,
#          depth_screen2_before=depth.x,
#          maf_screen2_before=maf.x,
#          ct_screen2_after=ct.y,
#          depth_screen2_after=depth.y,
#          maf_screen2_after=maf.y)%>%
#   dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))
# 
# screen_compare=merge(before_after_screen1,
#                      before_after_screen2,
#                      by=c("ref_aa","protein_start","alt_aa","ref","alt","alt_start_pos","consequence_terms","ref_codon","alt_codon","alt_codon_shortest","n_nuc_min"),
#                      all.x=T,
#                      all.y=T,suffixes = c("_screen1","_screen2"))
# 
# screen_compare=resmuts_adder(screen_compare)
# screen_compare=res_residues_adder(screen_compare)
# screen_compare=screen_compare%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))
# 
# screen_compare_means=screen_compare%>%
#   filter(!score_screen1%in%NA,!score_screen2%in%NA,!score_screen1%in%NaN,!score_screen2%in%NaN)%>%
#   rowwise()%>%
#   mutate(score_mean=mean(c(score_screen1,score_screen2)))

# write.csv(screen_compare_means,"Imat_Enrichment_bgmerged_2.22.23.csv")
##############

before_after_screen1=before_after_screen1%>%
  mutate(ct_screen1=ct.x)%>%
  dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))


before_after_screen2=before_after_screen2%>%
  mutate(ct_screen2=ct.x)%>%
  dplyr::select(-c("ct.x","depth.x","maf.x","totalcells.x","totalmutant.x","ct.y","depth.y","maf.y","totalcells.y","totalmutant.y"))

screen_compare=merge(before_after_screen1,
                     before_after_screen2,
                     by=c("ref_aa","protein_start","alt_aa","ref","alt","alt_start_pos","consequence_terms","ref_codon","alt_codon","alt_codon_shortest","n_nuc_min"),
                     all.x=T,
                     all.y=T)

screen_compare=resmuts_adder(screen_compare)
screen_compare=screen_compare%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep = ""))



plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,label=species,color=resmuts))+geom_text()+geom_abline()
ggplotly(plotly)


a=screen_compare%>%filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)
cor(a$score.x,a$score.y)

screen_compare_means=screen_compare%>%
  filter(!score.x%in%NA,!score.y%in%NA,!score.x%in%NaN,!score.y%in%NaN)%>%
  rowwise()%>%
  mutate(score_mean=mean(c(score.x,score.y)),
         score_weighteed_mean=weighted.mean(c(score.x,score.y),c(ct_screen1,ct_screen2)))

# write.csv(screen_compare_means,"Imatinib_Enrichment_2.20.23_v2.csv")

ggplot(screen_compare%>%filter(protein_start>=242,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=score.x))+geom_tile()
screen_compare=res_residues_adder(screen_compare)

plotly=ggplot(screen_compare,aes(x=score.x,y=score.y,label=species,color=resmuts))+geom_text()+geom_abline()
ggplotly(plotly)

plotly=ggplot(screen_compare%>%filter(!species%in%"T315I"),aes(x=score.x,y=score.y,label=species,color=resmuts))+geom_text()+geom_abline()
ggplotly(plotly)

ggplot(screen_compare%>%filter(!species%in%"T315I"),aes(x=score.x,y=score.y,label=species,color=resmuts))+geom_text()+geom_abline()+cleanup


plotly=ggplot(screen_compare,aes(x=netgr_obs.x,y=netgr_obs.y,label=species,color=resmuts))+geom_text()+geom_abline()
ggplotly(plotly)

screen_compare=screen_compare%>%filter(!score.x%in%c(NA,NaN),!score.y%in%c(NA,NaN))
screen_compare$density=get_density(x = screen_compare$score.x,y=screen_compare$score.y,n=50)
ggplot(screen_compare,aes(x=netgr_obs.x,y=netgr_obs.y,color=density))+
  geom_point()+
  scale_color_viridis_c()+
  # geom_jitter(position = position_jitter(width = 0.1, height = 0.1))+
  # scale_x_continuous(name="Score Replicate 1",limits=c(-5,5))+
  # scale_y_continuous(name="Score Replicate 2",limits=c(-5,5))+
  geom_abline(linetype="dashed")+
  theme(legend.position = "none")

a=screen_compare%>%filter(!score.x%in%c(NA,NaN),!score.y%in%c(NA,NaN))
cor(a$score.x,a$score.y)
# cor(a$netgr_obs.x,a$netgr_obs.y)


plotly=ggplot(screen_compare,aes(x=score.x,y=score.y))+
  geom_point(color="black",shape=21,aes(fill=resmuts))+geom_abline()
ggplotly(plotly)


ggplot(screen_compare,aes(x=score.x,y=score.y))+
  geom_point(color="black",shape=21,aes(fill=resmuts))+
  geom_abline()+
  scale_x_continuous(name="Score D0 D2")+
  scale_y_continuous(name="Score D0 D4")+
  labs(fill="Resistant\n Mutant")+
  scale_fill_manual(values=c("gray90","red"))

# ggsave("imatd0d2.d0d4_score_2.15.23.pdf",width=8,height=6,units="in",useDingbats=F)
```



IL3 Screens for plotting
Day 0 Day 2 vs Day 0 Day 4
```{r}
###### TSII Day 0 vs Day 2 #########

delta_t=48 #hours
cells_before=107 #total cells at before time point
cells_after=1515 #total cells at after time point
netgr=.055

before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane15/sample_3/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane16b/Sample9/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane16b/Sample10/sscs")
before_timepoint=variants_parser(before_timepoint,cells_before)

##########TSI Imatinib D2###########
# after_timepoint=merge_samples("Novogene_lane15/sample_6/sscs","Novogene_lane14/sample12/sscs")
# after_timepoint=merge_samples(after_timepoint,"Novogene_lane15/Sample_7/sscs")

##########TSI D2###########
after_timepoint=merge_samples("Novogene_lane13/Sample9/sscs","Novogene_lane13/Sample10/sscs")
# after_timepoint=merge_samples(after_timepoint,"Novogene_lane15/Sample_4/sscs")

####################

after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

# a=before_after%>%filter(protein_start%in%271)
```

```{r}
# a=before_after%>%filter(protein_start%in%271)
ggplot(before_after%>%filter(protein_start>=240,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=score))+geom_tile()


#####Focusing on conserved residues#####
ggplot(before_after%>%filter(protein_start%in%c(271,363,381:383)),aes(x=protein_start,y=alt_aa,fill=netgr_obs))+
  geom_tile()+
  theme(panel.background=element_rect(fill="white", colour="black"))+
  scale_fill_gradient2(low ="blue",midpoint=0,mid="white", high ="red",name="Enrichment Score")+
  scale_color_manual(values=c("black"))+scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,493),expand=c(0,0),breaks = c(248,250,256, 271,275,300,325,350,363,375,381,400,405,425,450,475))+
  ylab("Mutant Amino Acid")+
  theme(panel.grid.major.x = element_blank() ,
        panel.grid.major.y = element_blank() )

# ggsave("BCRABL_iL3Independence_D2_essential.pdf",height=6,width=24,units="in",useDingbats=F)



ggplot(before_after%>%filter(protein_start>=240,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=score))+
  geom_tile()+
  theme(panel.background=element_rect(fill="white", colour="black"))+
  scale_fill_gradient2(low ="blue",midpoint=0,mid="white", high ="red",name="Enrichment Score")+
  scale_color_manual(values=c("black"))+scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,493),expand=c(0,0),breaks = c(248,250,256, 271,275,300,325,350,363,375,381,400,405,425,450,475))+
  ylab("Mutant Amino Acid")+
  theme(panel.grid.major.x = element_blank() ,
        panel.grid.major.y = element_blank() )

# ggsave("BCRABL_iL3Independence_D2.pdf",height=6,width=24,units="in",useDingbats=F)
```



IMATINIB Screens for plotting
Day 0 Day 2 vs Day 0 Day 4
```{r}
###### TSII Day 0 vs Day 2 #########
source("code/merge_samples.R")
source("code/depth_finder.R")
delta_t=96 #hours
cells_before=370 #total cells at before time point
cells_after=10397 #total cells at after time point
netgr=.055

before_timepoint=merge_samples("Novogene_lane14/Sample10_combined/sscs","Novogene_lane13/sample7/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane14/sample11/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane15/sample_3/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane16b/Sample9/sscs")
before_timepoint=merge_samples(before_timepoint,"Novogene_lane16b/Sample10/sscs")
before_timepoint=variants_parser(before_timepoint,cells_before)

##########TSI Imatinib D2###########
after_timepoint=merge_samples("Novogene_lane15/sample_6/sscs","Novogene_lane14/sample12/sscs")
after_timepoint=merge_samples(after_timepoint,"Novogene_lane15/Sample_7/sscs")

##########TSI D2###########
# after_timepoint=merge_samples("Novogene_lane13/Sample9/sscs","Novogene_lane13/Sample10/sscs")
# after_timepoint=merge_samples(after_timepoint,"Novogene_lane15/Sample_4/sscs")

####################

after_timepoint=variants_parser(after_timepoint,cells_after)

before_after=compare_samples(before_timepoint,after_timepoint,netgr,delta_t)

# a=before_after%>%filter(protein_start%in%271)
# a=before_after%>%filter(protein_start%in%426)

```

```{r}
# a=before_after%>%filter(resmuts%in%T)
before_after=resmuts_adder(before_after)
before_after=res_residues_adder(before_after)

ggplot(before_after%>%filter(protein_start>=240,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=score))+geom_tile()


#####Focusing on RESISTANT residues#####
ggplot(before_after%>%filter(resmuts%in%T,!protein_start%in%"315"),aes(x=protein_start,y=alt_aa,fill=score))+
  geom_tile()+
  theme(panel.background=element_rect(fill="white", colour="black"))+
  scale_fill_gradient2(low ="blue",midpoint=0,mid="white", high ="red",name="Enrichment Score")+
  scale_color_manual(values=c("black"))+scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,493),expand=c(0,0),breaks=c(250,253,255,276,299,315,317,351,355,359,396,459,486))+
  ylab("Mutant Amino Acid")+
  theme(panel.grid.major.x = element_blank() ,
        panel.grid.minor.x = element_blank() ,
        panel.grid.major.y = element_blank() ,
        panel.grid.minor.y = element_blank() )

# ggsave("BCRABL_imatinib_D2_resistant.pdf",height=6,width=24,units="in",useDingbats=F)



ggplot(before_after%>%filter(protein_start>=240,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=score))+
  geom_tile()+
  theme(panel.background=element_rect(fill="white", colour="black"))+
  scale_fill_gradient2(low ="blue",midpoint=0,mid="white", high ="red",name="Enrichment Score")+
  scale_color_manual(values=c("black"))+scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,493),expand=c(0,0),breaks = c(248,250,256, 271,275,300,325,350,363,375,381,400,405,425,450,475))+
  ylab("Mutant Amino Acid")+
  theme(panel.grid.major.x = element_blank() ,
        panel.grid.minor.x = element_blank() ,
        panel.grid.major.y = element_blank() ,
        panel.grid.minor.y = element_blank() )

# ggsave("BCRABL_imat_D2.pdf",height=6,width=24,units="in",useDingbats=F)



ggplot(before_after%>%filter(protein_start>=240,protein_start<=494),aes(x=protein_start,y=alt_aa,fill=netgr_obs))+
  geom_tile()+
  theme(panel.background=element_rect(fill="white", colour="black"))+
  scale_fill_gradient2(low ="blue",midpoint=0.035,mid="white", high ="red",name="Net Growth Rate")+
  scale_color_manual(values=c("black"))+scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,493),expand=c(0,0),breaks = c(248,250,256, 271,275,300,325,350,363,375,381,400,405,425,450,475))+
  ylab("Mutant Amino Acid")+
  theme(panel.grid.major.x = element_blank() ,
        panel.grid.minor.x = element_blank() ,
        panel.grid.major.y = element_blank() ,
        panel.grid.minor.y = element_blank())+
  theme_dark()

a=before_after%>%filter(protein_start>=240,protein_start<=494,!ct.x%in%.5,!ct.y%in%.5)
median(a$netgr_obs)
ggplot(before_after%>%filter(protein_start>=240,protein_start<=494),aes(x=netgr_obs))+geom_histogram()
# ggsave("BCRABL_imat_D2_netgr.pdf",height=6,width=24,units="in",useDingbats=F)
```




