---
title: "ABL_SM_CRISPR_Cut_Analyses"
author: "Haider Inam"
date: '2023-03-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath(".."))

library(stringr)
library(dplyr)
library(ggplot2)
library(plotly)
library(tictoc)
library(doParallel)
library(foreach)
library(RColorBrewer)


# 

```

```{r}
#Cleanup code for plotting
source("code/plotting/cleanup.R")
```

```{r,eval=F}
source("code/variantcaller/add_l298l.R")
for(i in c(1:18)){
  sample=paste("sample",i,sep = "")
  # sample="sample1"
  
  input_df_nol298l=read.csv(paste("data/Consensus_Data/novogene_lane18/",sample,"/nol298l/duplex/variant_caller_outputs/variants_unique_ann.csv",sep=""))
  input_df_l298l=read.csv(paste("data/Consensus_Data/novogene_lane18/",sample,"/l298l/duplex/variant_caller_outputs/variants_unique_ann.csv",sep=""))
  
  output_df=add_l298l(input_df_nol298l,input_df_l298l)
  write.csv(output_df,
            paste("data/Consensus_Data/novogene_lane18/",sample,"/duplex/variant_caller_outputs/variants_unique_ann.csv",sep = ""))  
}

input_df_nol298l=read.csv("data/Consensus_Data/novogene_lane18/sample9/nol298l/duplex/variant_caller_outputs/variants_unique_ann.csv")
input_df_l298l=read.csv("data/Consensus_Data/novogene_lane18/sample9/l298l/duplex/variant_caller_outputs/variants_unique_ann.csv")
  
output_df=add_l298l(input_df_nol298l,input_df_l298l)
write.csv(output_df,"data/Consensus_Data/novogene_lane18/sample9/duplex/variant_caller_outputs/variants_unique_ann.csv")  

```

```{r, eval=F}
source("code/compare_screens.R")

source("code/plotting/cleanup.R")
source("code/plotting/heatmap_plotting_function.R")
# rm(list=ls())

comparisons=read.csv("data/Consensus_Data/novogene_lane18/TwistRegion1Screen_Comparisons_Todo.csv")
comparisons=comparisons%>%filter(Completed%in%"FALSE")

for(i in 1:nrow(comparisons)){
  # i=10
  dirname=comparisons$dirname[i]
  pathname=paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,sep = "")
  # Create directory if it doesn't already exist
  if (!file.exists(pathname)){
    dir.create(pathname)
} 
before_screen1_identifier=unlist(strsplit(comparisons$before_screen1_identifier[i],","))
after_screen1_identifier=unlist(strsplit(comparisons$after_screen1_identifier[i],","))
before_screen2_identifier=unlist(strsplit(comparisons$before_screen2_identifier[i],","))
after_screen2_identifier=unlist(strsplit(comparisons$after_screen2_identifier[i],","))
  # length(after_screen1_identifier)
# screen_compare_means=compare_screens(comparisons$before_screen1_identifier[i],
#                                      comparisons$after_screen1_identifier[i],
#                                      comparisons$before_screen2_identifier[i],
#                                      comparisons$after_screen2_identifier[i])
screen_compare_means=compare_screens(before_screen1_identifier,
                                     after_screen1_identifier,
                                     before_screen2_identifier,
                                     after_screen2_identifier)

screen_compare_means_forexport=apply(screen_compare_means,2,as.character)
# write.csv(screen_compare_means_forexport,file = paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/screen_comparison_",dirname,".csv",sep=""))

# Plot 1. What does the heatmap look like from the average of the net growth rate?
heatmap_plotting_function(screen_compare_means,242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot1_heatmap.pdf",sep=""),width=10,height=6,units="in",useDingbats=F)
# screen_compare_means2=screen_compare_means%>%filter(alt_codon%in%twist$Codon)

# Plot 2a: What do the correlations look like for net growth rate (show mutants in text)?
ggplot(screen_compare_means,aes(x=netgr_obs_screen1,y=netgr_obs_screen2,color=resmuts,label=species))+geom_text(size=2.5)+geom_abline()+cleanup+stat_cor(method = "pearson")+labs(color="Known\nResistant\nMutant")+scale_x_continuous("Net growth rate screen 1")+scale_y_continuous("Net growth rate screen 2")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2a_Netgrowthrate_correlations_text.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

# Plot 2b: What do the correlations look like for enrichment scores (show mutants in points)?
ggplot(screen_compare_means,aes(x=netgr_obs_screen1,y=netgr_obs_screen2,label=species))+geom_point(color="black",shape=21,size=2,aes(fill=resmuts))+geom_abline()+cleanup+stat_cor(method = "pearson")+labs(fill="Known\nResistant\nMutant")+scale_x_continuous("Net growth rate screen 1")+scale_y_continuous("Net growth rate screen 2")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2b_Netgrowthrate_correlations_points.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)
# Plot 2c: What do the correlations look like for enrichment scores (show mutants in text)?
ggplot(screen_compare_means,aes(x=score_screen1,y=score_screen2,color=resmuts,label=species))+geom_text(size=2.5)+geom_abline()+cleanup+ stat_cor(method = "pearson")+labs(color="Known\nResistant\nMutant")+scale_x_continuous("Enrichment score screen 1")+scale_y_continuous("Enrichment score screen 2")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot2c_Enrichmentscores_correlations_text.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

# Plot 3a: Plots: what are the overall net growth rate distributions?
ggplot(screen_compare_means,aes(x=netgr_obs_mean,fill=resmuts))+geom_density(alpha=0.7)+cleanup+labs(fill="Known\nResistant\nMutant")+scale_x_continuous("Mean net growth rate of screens")
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot3a_Netgrowthrate_distributions_resmuts.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)
# Plot 3b: Plots: what are the net growth rate distributions?

library(reshape2)
screen_compare_melt=melt(screen_compare_means%>%dplyr::select(species,netgr_obs_screen1,netgr_obs_screen2),id.vars = "species",measure.vars =c("netgr_obs_screen1","netgr_obs_screen2"),variable.name = "Condition",value.name = "netgr_obs")


ggplot(screen_compare_melt,aes(x=netgr_obs,fill=Condition))+
  geom_density(alpha=0.7)+
  cleanup+
  scale_x_continuous("Net growth rate observed")+
  scale_fill_discrete(labels=c("Screen 1","Screen 2"))
# ggsave(paste("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/",dirname,"/plot3b_Netgrowthrate_distributions.pdf",sep=""),width=6,height=4,units="in",useDingbats=F)

}

# dirname="K562_Medium_rep1vs2"

```


Doing some quick analyses on buried hydrophobic vs exposed residues

Quick analysis to do on the secondary structure:
The buried hydrophobic core is probably going to be more susceptible to polar/hydrophilic substitutions, and not as much to hydrophobic substitutions... do you see that in the il3 independence data? Answer: yes, I see a slight singal but it's not huge
```{r}
dssp=read.csv("data/DSSP_SolventAccessibility_ABL/2hyy_dspp.csv",header = T)
dssp=dssp%>%mutate(RESIDUE=as.numeric(RESIDUE),
                   ACC=as.numeric(ACC),AA=gsub("<ca>","",AA),
                   SS=case_when(STRUCTURE%in%c("E","B")~"b-sheet",
                                STRUCTURE%in%c("H","G","I")~"a-helix",
                                STRUCTURE%in%"T"~"turn",
                                T~"undefined"))%>%dplyr::select(-"STRUCTURE")

dssp=dssp%>%rename(protein_start=RESIDUE)

il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%dplyr::select(species,protein_start,netgr_obs_mean)
il3=il3%>%group_by(protein_start)%>%summarize(netgr_obs_mean=mean(netgr_obs_mean))

il3_dssp=merge(il3,dssp,by="protein_start")
il3_dssp=il3_dssp%>%mutate(exposed=case_when(ACC>=40~"Exposed",
                                            T~"Buried"))
# il3_dssp=il3_dssp%>%filter(exposed%in%"Exposed")
ggplot(il3_dssp,aes(x=ACC))+geom_histogram()



ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+
  cleanup+theme(legend.position = c(.9,.85))+
  theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)+theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v1.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  # facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+cleanup
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v2.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=ACC,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("DSSP Solvent Accessibility at Residue")+
  cleanup+
  labs(color="Solvent \nAccessibility")+
  theme(legend.position = c(.9,.25))+
  theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v3.pdf",width=6,height = 4,units="in",useDingbats=F)



il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%dplyr::select(species,ref_aa,protein_start,alt_aa,netgr_obs_mean)


il3_dssp=merge(il3,dssp,by.x=c("protein_start","ref_aa"),by.y=c("protein_start","AA"))
il3_dssp=il3_dssp%>%mutate(exposed=case_when(ACC>=40~"Exposed",
                                            T~"Buried"))

# il3_dssp=il3_dssp%>%mutate(hydrophobic=case_when(alt_aa%in%c("A","V","I","M","L","F","Y","W")~"hydrophobic",
#                                                  T~"other"))
ggplot(il3_dssp,aes(x=alt_aa,y=netgr_obs_mean))+geom_boxplot()+facet_wrap(~exposed)
ggplot(il3_dssp,aes(x=exposed,y=netgr_obs_mean))+geom_boxplot()+facet_wrap(~exposed)


ggplot(il3_dssp,aes(x=factor(protein_start),y=netgr_obs_mean,fill=exposed))+
  geom_boxplot()+
  # facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_discrete("Residue on the ABL Kinase")+
  labs(fill="Solvent \nAccessibility")+cleanup+
  theme(axis.text.x=element_text(angle=90, hjust=1))

```



Doing some quick analyses on buried hydrophobic vs exposed residues
```{r,eval=F,include=F}
dssp=read.csv("data/DSSP_SolventAccessibility_ABL/2gqg_dspp.csv",header = T)
dssp=dssp%>%mutate(RESIDUE=as.numeric(RESIDUE),ACC=as.numeric(ACC),AA=gsub("<ca>","",AA))
dssp=dssp%>%rename(protein_start=RESIDUE)

il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%select(species,protein_start,netgr_obs_mean)
il3=il3%>%group_by(protein_start)%>%summarize(netgr_obs_mean=mean(netgr_obs_mean))

il3_dssp=merge(il3,dssp,by="protein_start")
il3_dssp=il3_dssp%>%mutate(exposed=case_when(ACC>=40~"Exposed",
                                            T~"Buried"))
ggplot(il3_dssp,aes(x=ACC))+geom_histogram()



ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+
  cleanup+theme(legend.position = c(.9,.85))+
  theme(
  strip.background = element_blank(),
  strip.text.x = element_blank()
)+theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v1.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=protein_start,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  # facet_wrap(~exposed,nrow=2)+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("Residue on the ABL Kinase")+
  labs(color="Solvent \nAccessibility")+cleanup
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v2.pdf",width=6,height = 4,units="in",useDingbats=F)


ggplot(il3_dssp,aes(x=ACC,y=netgr_obs_mean,color=exposed))+
  geom_point()+
  scale_y_continuous("Mean net growth rate at residue")+
  scale_x_continuous("DSSP Solvent Accessibility at Residue")+
  cleanup+
  labs(color="Solvent \nAccessibility")+
  theme(legend.position = c(.9,.25))+
  theme(legend.background = element_rect(
                                  size=0.5, linetype="solid", 
                                  colour ="black"))
# ggsave("data/DSSP_SolventAccessibility_ABL/il3solvent_accessibility_v3.pdf",width=6,height = 4,units="in",useDingbats=F)
```
Doing some quick DDG analysis
```{r}
ddg=read.table("data/DDG_ABL/2hyy_ddg.tsv")
colnames(ddg)=c("species","ddg","ddg_sd")
ddg=ddg%>%mutate(protein_start=234+as.numeric(gsub("[^0-9]","",species)),
                 ref_aa=substr(species,1,1),
                 alt_aa=sub(".+(.)$", "\\1", species),
                 species=paste(ref_aa,protein_start,alt_aa,sep = ""))
# class(ddg$protein_start)
ddg=ddg%>%filter(protein_start%in%c(242:322))

il3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
il3=il3%>%select(species,protein_start,netgr_obs_mean)
ddgil3=merge(ddg,il3,by=c("species","protein_start"))
ggplot(ddgil3,aes(x=ddg,y=netgr_obs_mean))+geom_point()
ggplot(ddgil3,aes(x=ddg,y=netgr_obs_mean,label=species))+geom_text()
```

Comparing Fitness Scores with IC50 predictions
```{r}
source("code/resmuts_adder.R",include=F,eval=F)
ic50data_all_sum=read.csv("output/ic50data_all_confidence_intervals_raw_data.csv",row.names = 1)
imat=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_low_rep1vsrep2_ft/screen_comparison_baf3_Imat_low_rep1vsrep2_ft.csv")
# imat=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_Imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv")
imat=imat%>%select(species,ref_aa,protein_start,alt_aa,netgr_obs_mean)
# x=imat%>%filter(species%in%"V299L")
imat=resmuts_adder(imat)
resmuts_merged=merge(imat%>%filter(resmuts%in%"TRUE"),ic50data_all_sum%>%dplyr::select(species,netgr_pred_model,netgr_pred_mean),by="species")


ggplot(resmuts_merged,aes(x=netgr_pred_mean,y=netgr_obs_mean,label=species))+geom_text()+theme_bw()+geom_abline()
```


```{r}
#######################Making Correlation Plots for Paper################

###########Cross Species Correlations###########
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-species/baf3_Imat_Lowvsk562_Imat_Medium/screen_comparison_baf3_Imat_Lowvsk562_Imat_Medium.csv",header = T,stringsAsFactors = F)
source("code/res_residues_adder.R")
source("code/cosmic_data_adder.R")
# data=read.csv("output/ABLEnrichmentScreens/Imat_Enrichment_bgmerged_2.22.23.csv",header = T,stringsAsFactors = F)
# class(data)
data=res_residues_adder(data)
data=cosmic_data_adder(data)
# data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs.x,netgr_obs.y))
data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
data$resmut_cosmic="neither"
data[data$cosmic_present%in%TRUE,"resmut_cosmic"]="cosmic"
data[data$resmuts%in%TRUE,"resmut_cosmic"]="resmut"
data$resmut_cosmic=factor(data$resmut_cosmic,levels=c("neither","cosmic","resmut"))

ggplot(data%>%filter(protein_start>=242,protein_start<=322),aes(x=netgr_obs_screen1,y=netgr_obs_screen2))+
  geom_point(color="black",shape=21,size=.75,aes(fill=resmuts))+
  # geom_abline()+
  scale_x_continuous(name="Net Growth Rate Baf3")+
  scale_y_continuous(name="Net Growth Rate K562")+
  labs(fill="Sanger\n Mutant")+
  scale_fill_manual(values=c("gray90","red"))+
  cleanup+theme(legend.position = "none")+
  stat_cor(method="pearson")
# ggsave("output/SM_Imatinib_Plots/Baf3vsK562_ImatinibEnrichment_Plot_Medium_4.13.23.pdf",width=3,height=3,units="in",useDingbats=F)

###########K562s###########
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv",header = T,stringsAsFactors = F)
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv",header = T,stringsAsFactors = F)
source("code/res_residues_adder.R")
source("code/cosmic_data_adder.R")
# data=read.csv("output/ABLEnrichmentScreens/Imat_Enrichment_bgmerged_2.22.23.csv",header = T,stringsAsFactors = F)
# class(data)
data=res_residues_adder(data)
data=cosmic_data_adder(data)
# data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs.x,netgr_obs.y))
data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
data$resmut_cosmic="neither"
data[data$cosmic_present%in%TRUE,"resmut_cosmic"]="cosmic"
data[data$resmuts%in%TRUE,"resmut_cosmic"]="resmut"
data$resmut_cosmic=factor(data$resmut_cosmic,levels=c("neither","cosmic","resmut"))

# !ct_screen1_after%in%.5,!ct_screen2_after%in%.5,
ggplot(data%>%filter(protein_start>=242,protein_start<=322),aes(x=netgr_obs_screen1,y=netgr_obs_screen2))+
  geom_point(color="black",shape=21,size=.75,aes(fill=resmuts))+
  geom_abline()+
  scale_x_continuous(name="Net Growth Rate Rep 1")+
  scale_y_continuous(name="Net Growth Rate Rep 2")+
  labs(fill="Sanger\n Mutant")+
  scale_fill_manual(values=c("gray90","red"))+
  cleanup+theme(legend.position = "none")+
  stat_cor(method="pearson")
# ggsave("output/SM_Imatinib_Plots/K562_ImatinibEnrichment_Plot_Medium_4.13.23.pdf",width=3,height=3,units="in",useDingbats=F)

ggplot(data%>%filter(protein_start>=242,protein_start<=322),aes(x=netgr_obs_mean,fill=resmuts))+
  geom_density(alpha=.7)+scale_x_continuous(bquote('Net Growth Rate '(Hours^-1)))+scale_y_continuous("Density")+scale_fill_manual(values=c("gray","red"))+cleanup+theme(legend.position = "none")
# ggsave("output/SM_Imatinib_Plots/K562_Density_Imat_netgr_4.19.23.pdf",width=4,height=3,units="in",useDingbats=F)

ggplot(data%>%filter(!species%in%"V299L",protein_start>=242,protein_start<=322,n_nuc_min%in%1),aes(x=resmut_cosmic,y=netgr_mean,fill=resmut_cosmic))+
  # geom_violin(color="black")+
  geom_boxplot(color="black")+
  geom_jitter(color="black", size=1,width=.1, alpha=0.9)+
  scale_fill_manual(values=c("gray90","orange","red"))+scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+scale_x_discrete("Resistance Status",labels=c("Never\n Seen","Sanger","Known\nResistant"))+cleanup+theme(legend.position = "none")
ggsave("output/SM_Imatinib_Plots/ImatinibEnrichment_netgr_boxplot_k562s_4.21.23.pdf",width=3,height=3,units="in",useDingbats=F)
###########Baf3s###########

# data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_low_rep1vsrep2_ft/screen_comparison_baf3_Imat_low_rep1vsrep2_ft.csv",header = T,stringsAsFactors = F)
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_high_rep1vsrep2_ft/screen_comparison_baf3_Imat_high_rep1vsrep2_ft.csv",header = T,stringsAsFactors = F)
# data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv",header = T,stringsAsFactors = F)
source("code/res_residues_adder.R")
source("code/cosmic_data_adder.R")
# data=read.csv("output/ABLEnrichmentScreens/Imat_Enrichment_bgmerged_2.22.23.csv",header = T,stringsAsFactors = F)
# class(data)
data=res_residues_adder(data)
data=cosmic_data_adder(data)
# data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs.x,netgr_obs.y))
data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
data$resmut_cosmic="neither"
data[data$cosmic_present%in%TRUE,"resmut_cosmic"]="cosmic"
data[data$resmuts%in%TRUE,"resmut_cosmic"]="resmut"
data$resmut_cosmic=factor(data$resmut_cosmic,levels=c("neither","cosmic","resmut"))

# !ct_screen1_after%in%.5,!ct_screen2_after%in%.5,
ggplot(data%>%filter(protein_start>=242,protein_start<=322),aes(x=netgr_obs_screen1,y=netgr_obs_screen2))+
  geom_point(color="black",shape=21,size=.75,aes(fill=resmuts))+
  geom_abline()+
  scale_x_continuous(name="Net Growth Rate Rep 1")+
  scale_y_continuous(name="Net Growth Rate Rep 2")+
  labs(fill="Sanger\n Mutant")+
  scale_fill_manual(values=c("gray90","red"))+
  cleanup+theme(legend.position = "none")+
  stat_cor(method="pearson")
  
# ggsave("output/SM_Imatinib_Plots/BaF3_ImatinibEnrichment_Plot_Medium_4.13.23.pdf",width=3,height=3,units="in",useDingbats=F)

ggplot(data%>%filter(!species%in%"V299L",protein_start>=242,protein_start<=322),aes(x=netgr_obs_mean,fill=resmuts))+
  geom_density(alpha=.7)+scale_x_continuous(bquote('Net Growth Rate '(Hours^-1)))+scale_y_continuous("Density")+scale_fill_manual(values=c("gray","red"))+cleanup+theme(legend.position = "none")
# ggsave("output/SM_Imatinib_Plots/Baf3_Density_Imat_netgr_4.19.23.pdf",width=4,height=3,units="in",useDingbats=F)





ggplot(data%>%filter(protein_start>=242,protein_start<=494,n_nuc_min%in%1),aes(x=reorder(species,-netgr_obs_mean),y=netgr_obs_mean,fill=resmut_cosmic))+geom_col()+theme(axis.text.x=element_text(angle=90, hjust=1))+scale_y_continuous(name="Enrichcment Score")+scale_x_discrete(name="Mutant")+scale_fill_manual(name="Resistance Status",labels=c("Never Seen","Sanger Mutant","Known Resistant Mutant"),values=c("gray","orange","red"))+cleanup+theme(legend.position = "none")


ggplot(data%>%group_by(species)%>%mutate(n_species=n())%>%filter(protein_start>=242,protein_start<=494,n_species%in%1),aes(x=reorder(species,-netgr_mean),y=netgr_mean,fill=resmut_cosmic))+geom_col()+theme(axis.text.x=element_text(angle=90, hjust=1))+scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+scale_x_discrete(name="Mutant")+scale_fill_manual(name="Resistance Status",labels=c("Never Seen","Sanger Mutant","Known Resistant Mutant"),values=c("gray","orange","red"))+cleanup+theme(legend.position = "none")
# ggsave("ImatinibEnrichment_Netgr_Distribution.pdf",width=8,height=4,units="in",useDingbats=F)

ggplot(data%>%filter(protein_start>=242,protein_start<=494,n_nuc_min%in%1,score_mean>=0),aes(x=reorder(species,-netgr_mean),y=netgr_mean,fill=resmut_cosmic))+geom_col()+
  scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+
  scale_x_discrete(name="Mutant")+
  scale_fill_manual(name="Resistance Status",labels=c("Never Seen","Sanger Mutant","Known Resistant Mutant"),values=c("gray","orange","red"))+
  theme(axis.text.x=element_text(angle=90, hjust=1),
        axis.text=element_text(size=6),
        panel.grid.major = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank())+
  theme(legend.position = "none")
# ggsave("ImatinibEnrichment_Netgr_Distribution_zoom.pdf",width=6,height=4,units="in",useDingbats=F)


ggplot(data%>%filter(!species%in%"V299L",protein_start>=242,protein_start<=322,n_nuc_min%in%1),aes(x=resmut_cosmic,y=netgr_mean,fill=resmut_cosmic))+
  # geom_violin(color="black")+
  geom_boxplot(color="black")+
  geom_jitter(color="black", size=1,width=.1, alpha=0.9)+
  scale_fill_manual(values=c("gray90","orange","red"))+scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+scale_x_discrete("Resistance Status",labels=c("Never\n Seen","Sanger","Known\nResistant"))+cleanup+theme(legend.position = "none")
ggsave("output/SM_Imatinib_Plots/ImatinibEnrichment_netgr_boxplot_baf3s_4.21.23.pdf",width=3,height=3,units="in",useDingbats=F)

plotly=ggplot(data%>%filter(protein_start>=242,protein_start<=494,n_nuc_min%in%1),aes(x=reorder(species,-netgr_mean),y=netgr_mean,fill=resmut_cosmic))+geom_col()+theme(axis.text.x=element_text(angle=90, hjust=1))+scale_y_continuous(name="Enrichcment Score")+scale_x_discrete(name="Mutant")+guides(fill = guide_legend(title = "Clinically\n Observed \n Resmut"))+scale_fill_manual(values=c("gray","orange","red"))
ggplotly(plotly)



```
Looking at important sanger mutants across BaF3s and K562s
```{r}
# K562
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv",header = T,stringsAsFactors = F)
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv",header = T,stringsAsFactors = F)
# BAf3
# data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_high_rep1vsrep2_ft/screen_comparison_baf3_Imat_high_rep1vsrep2_ft.csv",header = T,stringsAsFactors = F)
source("code/res_residues_adder.R")
source("code/cosmic_data_adder.R")
# data=read.csv("output/ABLEnrichmentScreens/Imat_Enrichment_bgmerged_2.22.23.csv",header = T,stringsAsFactors = F)
# class(data)
data=res_residues_adder(data)
data=cosmic_data_adder(data)
# data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs.x,netgr_obs.y))
data=data%>%rowwise()%>%mutate(netgr_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
data$resmut_cosmic="neither"
data[data$cosmic_present%in%TRUE,"resmut_cosmic"]="cosmic"
data[data$resmuts%in%TRUE,"resmut_cosmic"]="resmut"
data$resmut_cosmic=factor(data$resmut_cosmic,levels=c("neither","cosmic","resmut"))
# x=data%>%filter(resmut_cosmic%in%"cosmic")

ggplot(data%>%filter(!species%in%"V299L",protein_start>=242,protein_start<=322,n_nuc_min%in%1),aes(x=resmut_cosmic,y=netgr_mean,fill=resmut_cosmic))+
  # geom_violin(color="black")+
  geom_boxplot(color="black")+
  geom_jitter(color="black", size=1,width=.1, alpha=0.9)+
  scale_fill_manual(values=c("gray90","orange","red"))+scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+scale_x_discrete("Resistance Status",labels=c("Never\n Seen","Sanger","Known\nResistant"))+cleanup+theme(legend.position = "none")
ggsave("output/SM_Imatinib_Plots/ImatinibEnrichment_netgr_boxplot_baf3s_4.21.23.pdf",width=3,height=3,units="in",useDingbats=F)

```
```{r}
# Analyzing the Sanger data 4.22.2023
sanger=read.csv("data/Cosmic_ABL/ABL_Cosmic_Gene_mutations.csv",header = T)
sanger=sanger%>%dplyr::rename(protein_start=Position,species=AA.Mutation,sanger.count=Count)%>%filter(Type%in%"Substitution - Missense")%>%dplyr::select(protein_start,species,sanger.count)
sanger=sanger%>%mutate(species=gsub("p.","",species),ref_aa=substring(species,1,1),
                       alt_aa=substring(species, nchar(species), nchar(species)))
sanger=sanger%>%mutate(sanger.present=T)
sanger=sanger%>%filter(protein_start%in%242:520)
# sanger=resmuts_adder(sanger)
sum(sanger[sanger$resmuts%in%T,"sanger.count"])
sum(sanger[sanger$resmuts%in%F,"sanger.count"])
# There are a total of 1884 patients with mutations in the kianse. 1193 of these patients have known clinically resistant ImatR mutations. However, 691 of these patients fall into the other category

# K562
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv",header = T,stringsAsFactors = F)
data=data%>%rowwise()%>%mutate(netgr_obs_mean.k562=mean(netgr_obs_screen1,netgr_obs_screen2),netgr_obs_sd.k562=sd(c(netgr_obs_screen1,netgr_obs_screen2)))
data.k562=data%>%dplyr::select(species,protein_start,ref_aa,alt_aa,n_nuc_min,netgr_obs_mean.k562,netgr_obs_sd.k562)
# Baf3
data=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_medium_rep1vsrep2_ft/screen_comparison_baf3_Imat_medium_rep1vsrep2_ft.csv",header = T,stringsAsFactors = F)
data=data%>%rowwise()%>%mutate(netgr_obs_mean.baf3=mean(netgr_obs_screen1,netgr_obs_screen2),netgr_obs_sd.baf3=sd(c(netgr_obs_screen1,netgr_obs_screen2)))
data.baf3=data%>%dplyr::select(species,protein_start,ref_aa,alt_aa,n_nuc_min,netgr_obs_mean.baf3,netgr_obs_sd.baf3)

data=merge(data.k562,data.baf3,by=c("species","protein_start","ref_aa","alt_aa","n_nuc_min"),all=T)
# data$sanger.present=F
# data$sanger.count=0
data=merge(data,sanger,by=c("species","protein_start","ref_aa","alt_aa"),all=T)

source("code/resmuts_adder.R")
data=resmuts_adder(data)

data=data%>%mutate(cosmic_present=sanger.present)
# data=data%>%mutate(alt_aa=substring(species, nchar(species), nchar(species)))
data$resmut_cosmic="neither"
data[data$cosmic_present%in%TRUE,"resmut_cosmic"]="cosmic"
data[data$resmuts%in%TRUE,"resmut_cosmic"]="resmut"
data$resmut_cosmic=factor(data$resmut_cosmic,levels=c("neither","cosmic","resmut"))


ggplot(data%>%filter(protein_start>=242,protein_start<=322),aes(x=resmut_cosmic,y=netgr_obs_mean.baf3,fill=resmut_cosmic))+
  # geom_violin(color="black")+
  geom_boxplot(color="black")+
  geom_jitter(color="black", size=.5,width=.1, alpha=0.9)+
  scale_fill_manual(values=c("gray90","orange","red"))+scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+scale_x_discrete("Resistance Status",labels=c("Never\n Seen","Rare\n VUDR","Known\n Resistant\n Variant"))+cleanup+theme(legend.position = "none")
# ggsave("output/SM_Imatinib_Plots/ImatinibEnrichment_netgr_boxplot_baf3s_4.21.23.pdf",width=3,height=3.5,units="in",useDingbats=F)

ggplot(data%>%filter(protein_start>=242,protein_start<=322),aes(x=resmut_cosmic,y=netgr_obs_mean.k562,fill=resmut_cosmic))+
  # geom_violin(color="black")+
  geom_boxplot(color="black")+
  geom_jitter(color="black", size=.5,width=.1, alpha=0.9)+
  scale_fill_manual(values=c("gray90","orange","red"))+scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+scale_x_discrete("Resistance Status",labels=c("Never\n Seen","Rare\n VUDR","Known\n Resistant\n Variant"))+cleanup+theme(legend.position = "none")
# ggsave("output/SM_Imatinib_Plots/ImatinibEnrichment_netgr_boxplot_k562s_4.21.23.pdf",width=3,height=3.5,units="in",useDingbats=F)

data.forttest=data%>%filter(protein_start>=242,protein_start<=322,n_nuc_min%in%1)
t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.baf3"],
       data.forttest[data.forttest$resmut_cosmic%in%"cosmic","netgr_obs_mean.baf3"])

t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.baf3"],
       data.forttest[data.forttest$resmut_cosmic%in%"resmut","netgr_obs_mean.baf3"])

t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.k562"],
       data.forttest[data.forttest$resmut_cosmic%in%"cosmic","netgr_obs_mean.k562"])

t.test(data.forttest[data.forttest$resmut_cosmic%in%"neither","netgr_obs_mean.k562"],
       data.forttest[data.forttest$resmut_cosmic%in%"resmut","netgr_obs_mean.k562"])


ggplot(data%>%filter(sanger.present%in%T,n_nuc_min%in%1),aes(x=netgr_obs_mean.baf3,y=netgr_obs_mean.k562))+
  geom_point()+
  stat_cor(method="pearson")

ggplot(data%>%filter(sanger.present%in%T,n_nuc_min%in%1),aes(x=netgr_obs_mean.baf3,y=netgr_obs_mean.k562,label=species,color=resmuts))+
  geom_text(size=1.6)+
  # stat_cor(method="pearson")+
  cleanup+
  scale_x_continuous("Net Growth Rate Baf3")+
  scale_y_continuous("Net Growth Rate K562")+
  scale_color_manual(values=c("orange","red"))+
  theme(legend.position = "none")
# ggsave("output/SM_Imatinib_Plots/baf3_k562_sanger_correlation.pdf",width=3,height=3,units = "in",useDingbats=F)



plotly=ggplot(data%>%filter(sanger.present%in%T,n_nuc_min%in%1),aes(x=netgr_obs_mean.baf3,y=netgr_obs_mean.k562,label=species,color=resmuts))+
  geom_text()+
  # stat_cor(method="pearson")+
  cleanup+
  scale_x_continuous("Net Growth Rate Baf3")+
  scale_y_continuous("Net Growth Rate K562")+
  scale_color_manual(values=c("orange","red"))+
  theme(legend.position = "none")
ggplotly(plotly)

x=data%>%filter(protein_start%in%c(242:322),n_nuc_min%in%1)%>%filter(resmut_cosmic%in%"neither")
x=data%>%filter(protein_start%in%c(242:322),n_nuc_min%in%1)%>%filter(resmut_cosmic%in%"cosmic")
x=data%>%filter(protein_start%in%c(242:322),n_nuc_min%in%1)%>%filter(resmut_cosmic%in%"cosmic")

# Making piechart that shows that VUDR take up 36%
sanger_forpiechart=resmuts_adder(sanger)
sanger_forpiechart$category="VUDR"
sanger_forpiechart=sanger_forpiechart%>%mutate(category=case_when(resmuts%in%T~species,
                                                                  T~category))



sanger_forpiechart=sanger_forpiechart%>%group_by(category)%>%summarize(count=sum(sanger.count))
sanger_forpiechart=sanger_forpiechart%>%arrange(desc(count))
sanger_forpiechart$category=factor(sanger_forpiechart$category,levels = as.character(sanger_forpiechart$category[order((sanger_forpiechart$count),decreasing = T)]))

#Plotting the normalized dose response curves
getPalette = colorRampPalette(brewer.pal(22, "Spectral"))

library(RColorBrewer)
library("NatParksPalettes")
ggplot(sanger_forpiechart,aes(x="",y=count,fill=category))+
  geom_bar(width=1,stat="identity")+
  coord_polar("y", start=0)+
  # theme_minimal()+
  theme_void()+
  # scale_fill_manual(values=natparks.pals("Yellowstone", 3))
  scale_fill_manual(values = getPalette(length(unique(sanger_forpiechart$category))))
# ggsave("output/SM_Imatinib_Plots/sanger_piechart.pdf",width=4,height=3,units="in",useDingbats=F)

pie(sanger_forpiechart$count, labels = sanger_forpiechart$category)
```


```{r}
ggplot(data%>%filter(species%in%c("L273M","F311L","V260L","P296R","D276E", "K247W")),aes(x=netgr_obs_mean.baf3,y=netgr_obs_mean.k562,label=species,color=resmuts))+
  geom_text(size=1.6)+
  # stat_cor(method="pearson")+
  cleanup+
  scale_x_continuous("Net Growth Rate Baf3")+
  scale_y_continuous("Net Growth Rate K562")+
  scale_color_manual(values=c("orange","red"))+
  theme(legend.position = "none")
```
Making histogram of top clinically prevalent sanger mutants
```{r}
library(forcats)
# Analyzing the Sanger data 4.22.2023
sanger=read.csv("data/Cosmic_ABL/ABL_Cosmic_Gene_mutations.csv",header = T)
sanger=sanger%>%dplyr::rename(protein_start=Position,species=AA.Mutation,sanger.count=Count)%>%filter(Type%in%"Substitution - Missense")%>%dplyr::select(protein_start,species,sanger.count)
sanger=sanger%>%mutate(species=gsub("p.","",species),ref_aa=substring(species,1,1),
                       alt_aa=substring(species, nchar(species), nchar(species)))
sanger=sanger%>%mutate(sanger.present=T)

sanger=sanger%>%group_by(species)%>%summarize(protein_start=mean(protein_start),sanger.count=sum(sanger.count))
sanger$resmuts=F
sanger[sanger$species%in%c("E355A","D276G","H396R","F317L","F359I","E459K","G250E","F359C","F359V","M351T","L248V","E355G","Q252H","Y253F","F486S","H396P","E255K","Y253H","T315I","E255V","M244V","V299L","L387M"),"resmuts"]=T


ggplot(sanger%>%filter(resmuts%in%T),aes(fct_reorder(species, -sanger.count),y=sanger.count,fill=resmuts))+
  geom_col(color="black",alpha=0.8)+
  scale_x_discrete("Mutant Name")+
  scale_y_continuous("Clinical Abundance")+
  scale_fill_manual(values=c("red"))+
  cleanup+
  theme(legend.position = "none",
        axis.text.x=element_text(angle=90,hjust=.5,vjust=.5),
        axis.title.x=element_blank())
ggsave("output/SM_Imatinib_Plots/clinical_abundance_zoom.pdf",width=5,height=3,units="in",useDingbats=F)

ggplot(sanger,aes(fct_reorder(species, -sanger.count),y=sanger.count,fill=resmuts))+
  geom_col(alpha=0.8)+
  scale_x_discrete("Mutant Name")+
  scale_y_continuous("Clinical Abundance")+
  scale_fill_manual(values=c("gray90","red"))+
  # cleanup+
  theme(legend.position = "none",
        axis.text.x=element_text(size=2,angle=90,hjust=.5,vjust=.5),
        axis.title.x=element_blank())
ggsave("output/SM_Imatinib_Plots/clinical_abundance.pdf",width=14,height=3,units="in",useDingbats=F)

ggplot(sanger,aes(fct_reorder(species, -sanger.count),y=sanger.count,fill=resmuts))+
  geom_col()+
  scale_x_discrete("Mutant Name")+
  scale_y_continuous("Clinical Abundance")+
  scale_fill_manual(values=c("gray90","red"))+
  theme(legend.position = "none",
        axis.text.x=element_text(angle=90,hjust=.5,vjust=.5),
        axis.title.x=element_blank())

```



Heatmaps
```{r}
heatmap_plotting_function(smdata,290,297,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")+
  scale_x_continuous(name="",expand=c(0,0),breaks=c(290:297),labels=c("290","291","292","293","294","295","296","297"))+
  scale_fill_gradient(low ="darkblue", high ="red",name="Net growth rate")+theme(legend.position = "none",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region123_MergedwithOlddata/IL3_Enrichment_bgmerged_4.19.23.csv")
# Baf3s
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_low_rep1vsrep2_ft/screen_comparison_baf3_Imat_low_rep1vsrep2_ft.csv")
smdata=smdata%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))

heatmap_plotting_function(smdata%>%mutate(netgr_obs_mean=case_when(netgr_obs_mean>=.06~.06,
                                                    T~netgr_obs_mean)),242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")+
  scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,321),expand=c(0,0))+
  # scale_fill_gradient2(low ="darkblue",mid = "white",midpoint=0.04, high ="red",name="Net growth rate")+
  # scale_fill_gradient(low ="lightblue", high ="red",name="Net growth rate")+
  scale_fill_gradient2(low="blue",mid ="#9999FF",midpoint=.035, high ="red",name="Net growth rate")+theme(legend.position = "none")

ggsave("output/SM_Imatinib_Plots/heatmap_Imatinib_baf3.pdf",width=6,height = 4,units = "in",useDingbats=F)

####### K562 Low#######
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_low_rep1vsrep2/screen_comparison_k562_imat_low_rep1vsrep2.csv")
smdata=smdata%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))

heatmap_plotting_function(smdata%>%mutate(netgr_obs_mean=case_when(netgr_obs_mean>=.045~.045,
                                                    T~netgr_obs_mean)),242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")+
  scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,321),expand=c(0,0))+
  # scale_fill_gradient2(low ="darkblue",mid = "white",midpoint=0.04, high ="red",name="Net growth rate")+
  # scale_fill_gradient(low ="lightblue", high ="red",name="Net growth rate")+
  scale_fill_gradient2(low="blue",mid ="#9999FF",midpoint=.02, high ="red",name="Net growth rate")+theme(legend.position = "none")

ggsave("output/SM_Imatinib_Plots/heatmap_Imatinib_k562low.pdf",width=6,height = 4,units = "in",useDingbats=F)


####### K562 Medium#######
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv")
smdata=smdata%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))


heatmap_plotting_function(smdata,242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")

heatmap_plotting_function(smdata,242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")+
  scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,321),expand=c(0,0))+
  # scale_fill_gradient2(low ="darkblue",mid = "white",midpoint=0.04, high ="red",name="Net growth rate")+
  # scale_fill_gradient(low ="lightblue", high ="red",name="Net growth rate")+
  scale_fill_gradient2(low="blue",mid ="#9999FF",midpoint=0, high ="red",name="Net growth rate")+theme(legend.position = "none")

ggsave("output/SM_Imatinib_Plots/heatmap_Imatinib_k562med.pdf",width=6,height = 4,units = "in",useDingbats=F)


####### K562 High#######
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_high_rep1vsrep2/screen_comparison_k562_imat_high_rep1vsrep2.csv")
smdata=smdata%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))


heatmap_plotting_function(smdata,242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")

heatmap_plotting_function(smdata,242,321,fill_variable = "netgr_obs_mean",fill_name = "Net growth rate")+
  scale_x_continuous(name="Residue on the ABL Kinase",limits=c(242,321),expand=c(0,0))+
  # scale_fill_gradient2(low ="darkblue",mid = "white",midpoint=0.04, high ="red",name="Net growth rate")+
  # scale_fill_gradient(low ="lightblue", high ="red",name="Net growth rate")+
  scale_fill_gradient2(low="blue",mid ="#9999FF",midpoint=-0.005, high ="red",name="Net growth rate")+theme(legend.position = "none")

ggsave("output/SM_Imatinib_Plots/heatmap_Imatinib_k562high.pdf",width=6,height = 4,units = "in",useDingbats=F)
```

```{r}
smdata.k562=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_high_rep1vsrep2/screen_comparison_k562_imat_high_rep1vsrep2.csv")
# smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_low_rep1vsrep2/screen_comparison_k562_imat_low_rep1vsrep2.csv")
# smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/k562_imat_medium_rep1vsrep2/screen_comparison_k562_imat_medium_rep1vsrep2.csv")
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_low_rep1vsrep2_ft/screen_comparison_baf3_imat_low_rep1vsrep2_ft.csv")
# smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_medium_rep1vsrep2_ft/screen_comparison_baf3_imat_medium_rep1vsrep2_ft.csv")
# smdata.baf3=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_high_rep1vsrep2_ft/screen_comparison_baf3_imat_high_rep1vsrep2_ft.csv")
smdata.baf3=cosmic_data_adder(smdata.baf3)
smdata.k562=cosmic_data_adder(smdata.k562)

smdata.baf3=smdata%>%filter(!species%in%"V299L")
smdata.baf3=smdata.baf3%>%filter(n_nuc_min%in%1)
smdata.k562=smdata.k562%>%filter(n_nuc_min%in%1)

smdata.baf3=smdata.baf3%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
smdata.baf3=smdata.baf3%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
# Demonstrating that the SM data works better at predicting residue exposure than the BE data
# smdata_roc=smdata%

# glm.fit.sm=glm(as.numeric(smdata$cosmic_present)~smdata$netgr_obs_mean,family=binomial)

glm.fit.baf3=glm(as.numeric(smdata.baf3$resmuts)~smdata.baf3$netgr_obs_mean,family=binomial)
glm.fit.k562=glm(as.numeric(smdata.k562$resmuts)~smdata.k562$netgr_obs_mean,family=binomial)
smdata.baf3$glm_fits=glm.fit.baf3$fitted.values
smdata.k562$glm_fits=glm.fit.k562$fitted.values
# roc(as.numeric(smdata$cosmic_present),smdata$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True
#     Positive Percentage",print.auc=T)
roc(as.numeric(smdata.baf3$resmuts),smdata.baf3$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T)
roc(as.numeric(smdata.k562$resmuts),smdata.k562$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T)
# The GLM in this case looks a little weird, probably because there are so many negative datapoints
# ggplot(smdata.baf3,aes(x=netgr_obs_mean,y=as.numeric(resmuts)))+geom_point()+geom_line(aes(x=netgr_obs_mean,y=glm_fits))
# ggplot(smdata.k562,aes(x=netgr_obs_mean,y=as.numeric(resmuts)))+geom_point()+geom_line(aes(x=netgr_obs_mean,y=glm_fits))

par(pty="s")
roc(as.numeric(smdata.baf3$resmuts),smdata.baf3$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T,col="#3937E3",lwd=4)

# plot.roc(as.numeric(be_lfc.sm$DSSP.Buried),be_lfc.sm$glm_fits,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T,col="#378BE3",add=T,lwd=4,print.auc.y=45)
plot.roc(as.numeric(smdata.k562$resmuts),smdata.k562$glm_fits,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T,col="#378BE3",add=T,lwd=4,print.auc.y=45)
par(pty="m")
```

Doing quick correlation of lane 18b sample 4 NGS vs SSCS
```{r}
ngs=read.csv("data/Consensus_Data/novogene_lane18/sample4/ngs/variant_caller_outputs/variants_unique_ann.csv")
ngs=ngs%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf)
sscs=read.csv("data/Consensus_Data/novogene_lane18/sample4/sscs/variant_caller_outputs/variants_unique_ann.csv")
sscs=sscs%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf)

ngs_sscs=merge(ngs,sscs,by=c("ref_aa","protein_start","alt_aa","alt_codon"))
ngs_sscs=ngs_sscs%>%mutate(species=paste(ref_aa,protein_start,alt_aa,sep=""))
# ngs_sscs=ngs_sscs%>%filter(alt_codon%in%twist_alt_codon)

# plotly=ggplot(ngs_sscs,aes(x=maf.x,y=maf.y))+geom_point()+scale_x_continuous("NGS",trans="log10")+scale_y_continuous("SSCS",trans="log10")
# ggplotly(plotly)

plotly=ggplot(ngs_sscs,aes(x=maf.x,y=maf.y,label=species))+geom_text()+scale_x_continuous("NGS",trans="log10")+scale_y_continuous("SSCS",trans="log10")+geom_abline()
ggplotly(plotly)

plotly=ggplot(ngs_sscs,aes(x=maf.x,y=maf.y,label=species))+geom_text()+scale_x_continuous("NGS")+scale_y_continuous("SSCS")+geom_abline()
ggplotly(plotly)

x=ngs%>%filter(protein_start%in%255,alt_aa%in%"L",alt_codon%in%"CTG")
x=ngs_sscs%>%filter(species%in%"E255L")
codon_table=read.csv("data/codon_table.csv",header = T,stringsAsFactors = F)

  twist_codons=codon_table%>%filter(Twist%in%T)
  twist_alt_codon=twist_codons[twist_codons$Letter%in%alt_aa,"Codon"]
```
```{r}
sample10=read.csv("data/Consensus_Data/novogene_lane18/sample10/ngs/variant_caller_outputs/variants_unique_ann.csv")
# sample10=sample10%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf.d0=maf)
sample10=sample10%>%
  # filter(protein_start%in%c(242:272))%>%
  filter(protein_start%in%c(242:322))%>%
  mutate(maf=ct/depth,
         species=paste(ref_aa,protein_start,alt_aa,sep=""))%>%
  dplyr::select(type,ref_aa,protein_start,alt_aa,alt_codon,species,maf.d0=maf)
sample10=sample10%>%filter(alt_codon%in%twist_alt_codon)%>%
  group_by(type,ref_aa,protein_start,alt_aa,alt_codon,species)%>%
  summarize(maf.d0=max(maf.d0))

sample4=read.csv("data/Consensus_Data/novogene_lane18/sample4/ngs/variant_caller_outputs/variants_unique_ann.csv")
sample4=sample4%>%
  # filter(protein_start%in%c(242:272))%>%
  filter(protein_start%in%c(242:322))%>%
  mutate(maf=ct/depth,
         species=paste(ref_aa,protein_start,alt_aa,sep=""))%>%
  dplyr::select(type,ref_aa,protein_start,alt_aa,alt_codon,species,maf.screen1=maf)
sample4=sample4%>%filter(alt_codon%in%twist_alt_codon)%>%
  group_by(type,ref_aa,protein_start,alt_aa,alt_codon,species)%>%
  summarize(maf.screen1=max(maf.screen1))


sample5=read.csv("data/Consensus_Data/novogene_lane18/sample5/ngs/variant_caller_outputs/variants_unique_ann.csv")
sample5=sample5%>%
  # filter(protein_start%in%c(242:272))%>%
  filter(protein_start%in%c(242:322))%>%
  mutate(maf=ct/depth,
         species=paste(ref_aa,protein_start,alt_aa,sep=""))%>%
  dplyr::select(type,ref_aa,protein_start,alt_aa,alt_codon,species,maf.screen2=maf)
sample5=sample5%>%filter(alt_codon%in%twist_alt_codon)%>%
  group_by(type,ref_aa,protein_start,alt_aa,alt_codon,species)%>%
  summarize(maf.screen2=max(maf.screen2))


# sample5=sample5%>%filter(protein_start%in%c(242:272))%>%mutate(maf=ct/depth)%>%dplyr::select(ref_aa,protein_start,alt_aa,alt_codon,maf.screen2=maf)

baf3_low=merge(sample10,sample4,by=c("type","ref_aa","protein_start","alt_aa","alt_codon"))
baf3_low=merge(baf3_low,sample5,by=c("type","ref_aa","protein_start","alt_aa","alt_codon"))
# baf3_low=baf3_low%>%filter(alt_codon%in%twist_alt_codon)
baf3_low=baf3_low%>%mutate(netgr_screen1=log(maf.screen1*25546/(maf.d0*54))/144,
                           netgr_screen2=log(maf.screen2*22471/(maf.d0*54))/144)

plotly=ggplot(baf3_low,aes(x=netgr_screen1,y=netgr_screen2))+geom_point()+scale_x_continuous(trans="log10")+scale_y_continuous(trans="log10")+facet_wrap(~type)
ggplotly(plotly)
source("code/resmuts_adder.R")
baf3_low=resmuts_adder(baf3_low)
plotly=ggplot(baf3_low,aes(x=netgr_screen1,y=netgr_screen2,label=species,color=resmuts))+geom_text()+scale_x_continuous(trans="log10")+scale_y_continuous(trans="log10")
ggplotly(plotly)
cor(baf3_low$netgr_screen1,baf3_low$netgr_screen2)

class(baf3_low$netgr_screen1)
baf3_low=baf3_low%>%mutate(netgr_obs_mean=(netgr_screen1+netgr_screen2)/2)

glm.fit.baf3=glm(as.numeric(baf3_low$resmuts)~baf3_low$netgr_obs_mean,family=binomial)
baf3_low$glm_fits=glm.fit.baf3$fitted.values
roc(as.numeric(baf3_low$resmuts),baf3_low$glm_fits,plot=T,legacy.axes=T,percent=T,xlab="False Positive Percentage",ylab="True Positive Percentage",print.auc=T)

baf3_low2=baf3_low%>%filter(!protein_start%in%c(289:306))%>%dplyr::select(ref_aa,protein_start,alt_aa,species,netgr_obs_mean)
# baf3_low=
  
smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_low_rep1vsrep2_ft/screen_comparison_baf3_imat_low_rep1vsrep2_ft.csv")
smdata=smdata%>%filter(!ct_screen1_after%in%.5,!ct_screen1_after%in%.5)
smdata=smdata%>%filter(!protein_start%in%c(289:306))%>%dplyr::select(ref_aa,protein_start,alt_aa,species,netgr_obs_mean)

  
baf3_low2=merge(baf3_low2,smdata,by=c("ref_aa","protein_start","alt_aa","species"),all = T)
baf3_low2=baf3_low2%>%filter(!ref_aa==alt_aa)
baf3_low2$ngsonly=F
baf3_low2[baf3_low2$netgr_obs_mean.y%in%NA,"ngsonly"]=T
baf3_low2[baf3_low2$netgr_obs_mean.y%in%NA,"netgr_obs_mean.y"]=.01
  
ggplot(baf3_low2,aes(x=netgr_obs_mean.x,y=netgr_obs_mean.y,label=species,color=ngsonly))+geom_text()+stat_cor(method = "pearson")
x=baf3_low2%>%filter(netgr_obs_mean.y%in%NA)

smdata=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_imat_low_rep1vsrep2_ft/screen_comparison_baf3_imat_low_rep1vsrep2_ft.csv")
ggplot(smdata,aes(x=ct_screen1_after,y=netgr_obs_mean))+geom_point()+scale_x_continuous(trans="log10")
```




Merging ABL Lane 18 dataset
```{r,include=F,eval=F}
######## Merging the two ABL dataframes########
################IL3##############
# data_old=read.csv("bcrabl_il3d0d4_scores.csv",header = T,stringsAsFactors = F)
data_old=read.csv("output/ABLEnrichmentScreens/IL3_Enrichment_bgmerged_2.20.23.csv",header = T,stringsAsFactors = F)
data_old=data_old%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
data_old=data_old%>%filter(protein_start%in%c(323:494))
data_new=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv",header = T,stringsAsFactors = F)
data_sum=data_new%>%group_by(n_nuc_min)%>%summarize(ct=n())
data_new=data_new%>%filter(protein_start%in%c(242:322))
data_merged=rbind(data_new,data_old)
# write.csv(data_merged,"output/ABLEnrichmentScreens/ABL_Region123_MergedwithOlddata/IL3_Enrichment_bgmerged_4.19.23.csv")
################Imatinib##############
data_old=read.csv("output/ABLEnrichmentScreens/Imat_Enrichment_bgmerged_2.22.23.csv",header = T,stringsAsFactors = F)
data_old=data_old%>%rowwise()%>%mutate(netgr_obs_mean=mean(netgr_obs_screen1,netgr_obs_screen2))
data_old=data_old%>%filter(protein_start%in%c(323:494))
data_new=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_low_rep1vsrep2_ft/screen_comparison_baf3_Imat_low_rep1vsrep2_ft.csv",header = T,stringsAsFactors = F)
data_new=data_new%>%filter(protein_start%in%c(242:322))
data_merged=rbind(data_new,data_old)
# write.csv(data_merged,"output/ABLEnrichmentScreens/ABL_Region123_MergedwithOlddata/Imat_Enrichment_bgmerged_4.19.23.csv")
```

Plotting the short et al data for Twinstrand
```{r}
mean(data_new$netgr_obs_mean)
#################################
short_mutants=read.csv("data/Short_et_al_fig1/short_et_al_3.12.23.csv",header = T)
short_mutants$preexisting_all=T
short_mutants=short_mutants%>%dplyr::select(-Index)%>%rename(species=Species)
data_merged=merge(data_merged,short_mutants,by="species",all.x = T)
data_merged[!data_merged$preexisting_all%in%T,"preexisting_all"]=F
nrow(data_merged%>%filter(preexisting_all%in%T))
# source("code/resmuts_adder.R")
data_merged=resmuts_adder(data_merged)
data_merged$resmut_cosmic="neither"
data_merged[data_merged$preexisting_all%in%TRUE,"resmut_cosmic"]="preexisting"
data_merged[data_merged$resmuts%in%TRUE,"resmut_cosmic"]="resmut"
data_merged$resmut_cosmic=factor(data_merged$resmut_cosmic,levels=c("neither","preexisting","resmut"))


ggplot(data_merged%>%filter(n_nuc_min%in%1),aes(x=resmut_cosmic,y=netgr_obs_mean,fill=resmut_cosmic))+
  geom_violin(color="black")+
  # geom_boxplot(color="black")+
  geom_jitter(color="black", size=.5,width=.1, alpha=0.9)+
  scale_fill_manual(values=c("gray90","gray50","red"))+scale_y_continuous(name=bquote('Net Growth Rate '(Hours^-1)))+scale_x_discrete("",labels=c("Undetected","Pre-existing\n ALL","Known\nResistant\n Variant"))+cleanup+theme(legend.position = "none")

# ggsave("data/Short_et_al_fig1/shortetal_netgr_BoxPlot_4.14.23.pdf",width=4,height=4,units="in",useDingbats=F)
# ggsave("output/SM_Imatinib_Plots/shortetal_netgr_BoxPlot_4.14.23.pdf",width=3,height=3,units="in",useDingbats=F)
x=short_mutants%>%filter(!Classification%in%"Silent")
x=data_merged%>%filter(protein_start%in%c(242:322),preexisting_all%in%T)
x=data_merged%>%filter(protein_start>=242,protein_start<=322,n_nuc_min%in%1,preexisting_all%in%T,resmuts%in%F)
x=data_merged%>%filter(n_nuc_min%in%1,preexisting_all%in%T,resmuts%in%F)
```


```{r}
bi=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
bi$dose=0
bi=bi%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_mean)

bl=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_low_rep1vsrep2/screen_comparison_baf3_Imat_low_rep1vsrep2.csv")
bl$dose=300
bl=bl%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_mean)

bm=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_medium_rep1vsrep2/screen_comparison_baf3_Imat_medium_rep1vsrep2.csv")
bm$dose=600
bm=bm%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_mean)


bh=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_high_rep1vsrep2/screen_comparison_baf3_Imat_high_rep1vsrep2.csv")
bh$dose=1200
bh=bh%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_mean)

b_merged=merge(bl,bm,by = c("ref_aa","protein_start","alt_aa","species"),suffixes = c(".low",".medium"))

b_merged=merge(b_merged,bh%>%rename(dose.high=dose,netgr_obs_mean.high=netgr_obs_mean),by = c("ref_aa","protein_start","alt_aa","species"))

b_merged=merge(b_merged,bi%>%rename(dose.il3=dose,netgr_obs_mean.il3=netgr_obs_mean),by = c("ref_aa","protein_start","alt_aa","species"))
source("code/cosmic_data_adder.R")
b_merged=cosmic_data_adder(b_merged)
b_merged=resmuts_adder(b_merged)

# write.csv(b_merged,"output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/baf3_smscreen_netgrowthrates_582023.csv")
# x=b_merged%>%filter(cosmic_present%in%T)
# kl=kl%>%mutate(netgr_obs_mean=netgr_obs_screen1)

# kl=cosmic_data_adder(kl)

```
6.2.2022
I am adding replicate level growth rates for Scott to use
```{r}
bi=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
bi$dose=0
bi=bi%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_rep1=netgr_obs_screen1,netgr_obs_rep2=netgr_obs_screen2)

bl=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_low_rep1vsrep2/screen_comparison_baf3_Imat_low_rep1vsrep2.csv")
bl$dose=300
bl=bl%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_rep1=netgr_obs_screen1,netgr_obs_rep2=netgr_obs_screen2)

bm=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_medium_rep1vsrep2/screen_comparison_baf3_Imat_medium_rep1vsrep2.csv")
bm$dose=600
bm=bm%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_rep1=netgr_obs_screen1,netgr_obs_rep2=netgr_obs_screen2)


bh=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_high_rep1vsrep2/screen_comparison_baf3_Imat_high_rep1vsrep2.csv")
bh$dose=1200
bh=bh%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,netgr_obs_rep1=netgr_obs_screen1,netgr_obs_rep2=netgr_obs_screen2)

b_merged=merge(bl,bm,by = c("ref_aa","protein_start","alt_aa","species"),suffixes = c(".low",".medium"))

b_merged=merge(b_merged,bh%>%rename(dose.high=dose,netgr_obs_rep1.high=netgr_obs_rep1,netgr_obs_rep2.high=netgr_obs_rep2),by = c("ref_aa","protein_start","alt_aa","species"))

b_merged=merge(b_merged,bi%>%rename(dose.il3=dose,netgr_obs_rep1.il3=netgr_obs_rep1,netgr_obs_rep2.il3=netgr_obs_rep2),by = c("ref_aa","protein_start","alt_aa","species"))
source("code/cosmic_data_adder.R")
source("code/resmuts_adder.R")
b_merged=cosmic_data_adder(b_merged)
b_merged=resmuts_adder(b_merged)

write.csv(b_merged,"output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/baf3_smscreen_netgrowthrates_622023.csv")
# x=b_merged%>%filter(cosmic_present%in%T)
# kl=kl%>%mutate(netgr_obs_mean=netgr_obs_screen1)

# kl=cosmic_data_adder(kl)

```


```{r}
bi=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_IL3_rep1vsrep2_ft/screen_comparison_baf3_IL3_low_rep1vsrep2_ft.csv")
bi$dose=0
bi=bi%>%mutate(lfc_rep1=log2(maf_screen1_after/maf_screen1_before),lfc_rep2=log2(maf_screen2_after/maf_screen2_before))
bi=bi%>%dplyr::select(ref_aa,protein_start,alt_aa,species,n_nuc_min,dose,lfc_rep1,lfc_rep2)

bl=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_low_rep1vsrep2/screen_comparison_baf3_Imat_low_rep1vsrep2.csv")
bl$dose=300
bl=bl%>%mutate(lfc_rep1=log2(maf_screen1_after/maf_screen1_before),lfc_rep2=log2(maf_screen2_after/maf_screen2_before))
bl=bl%>%dplyr::select(ref_aa,protein_start,alt_aa,species,n_nuc_min,dose,lfc_rep1,lfc_rep2)
# bl=bl%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,lfc_obs_rep1=lfc_obs_screen1,lfc_obs_rep2=lfc_obs_screen2)

bm=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_medium_rep1vsrep2/screen_comparison_baf3_Imat_medium_rep1vsrep2.csv")
bm$dose=600
bm=bm%>%mutate(lfc_rep1=log2(maf_screen1_after/maf_screen1_before),lfc_rep2=log2(maf_screen2_after/maf_screen2_before))
bm=bm%>%dplyr::select(ref_aa,protein_start,alt_aa,species,n_nuc_min,dose,lfc_rep1,lfc_rep2)
# bm=bm%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,lfc_obs_rep1=lfc_obs_screen1,lfc_obs_rep2=lfc_obs_screen2)


bh=read.csv("output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/cross-replicate/baf3_Imat_high_rep1vsrep2/screen_comparison_baf3_Imat_high_rep1vsrep2.csv")
bh$dose=1200
bh=bh%>%mutate(lfc_rep1=log2(maf_screen1_after/maf_screen1_before),lfc_rep2=log2(maf_screen2_after/maf_screen2_before))
bh=bh%>%dplyr::select(ref_aa,protein_start,alt_aa,species,n_nuc_min,dose,lfc_rep1,lfc_rep2)
# bh=bh%>%dplyr::select(ref_aa,protein_start,alt_aa,species,dose,lfc_obs_rep1=lfc_obs_screen1,lfc_obs_rep2=lfc_obs_screen2)

b_merged=merge(bl,bm,by = c("ref_aa","protein_start","alt_aa","species","n_nuc_min"),suffixes = c(".low",".medium"))

b_merged=merge(b_merged,bh%>%rename(dose.high=dose,lfc_rep1.high=lfc_rep1,lfc_rep2.high=lfc_rep2),by = c("ref_aa","protein_start","alt_aa","species","n_nuc_min"))

b_merged=merge(b_merged,bi%>%rename(dose.il3=dose,lfc_rep1.il3=lfc_rep1,lfc_rep2.il3=lfc_rep2),by = c("ref_aa","protein_start","alt_aa","species","n_nuc_min"))
source("code/cosmic_data_adder.R")
source("code/resmuts_adder.R")
b_merged=cosmic_data_adder(b_merged)
b_merged=resmuts_adder(b_merged)

# write.csv(b_merged,"output/ABLEnrichmentScreens/ABL_Region1_Lane18_Comparisons/baf3_smscreen_lfc_682023.csv")
# x=b_merged%>%filter(cosmic_present%in%T)
# kl=kl%>%mutate(netgr_obs_mean=netgr_obs_screen1)

# kl=cosmic_data_adder(kl)

```
