---
title: "clinical_abundance_predictions"
author: "Haider Inam"
date: "4/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# rm(list=ls())
library("lmtest")
# install.packages("ggplot2")
# update.packages("ggplot2")
library("ggplot2")
library("MASS")
library("fitdistrplus")
library("lme4")
library("boot")
library("dplyr")
library("plotly")
######################Cleanup for GGPlot2#########################################
cleanup=theme_bw() +
  theme(plot.title = element_text(hjust=.5),
        panel.grid.major = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(color = "black"),
        axis.text = element_text(face="bold",color="black",size="11"),
        text=element_text(size=11,face="bold"),
        axis.title=element_text(face="bold",size="11"))

###Downloading mutation bias data. Source of this data: https://github.com/pritchardlabatpsu/SurvivalOfTheLikeliest/tree/master/Figures/Figure3
compicmut=read.csv("../data/Combined_data_frame_IC_Mutprob_abundance.csv",header=T,stringsAsFactors=F)
# compicmut=read.csv("data/Combined_data_frame_IC_Mutprob_abundance.csv",header=T,stringsAsFactors=F)

twinstrand_simple_melt_merge=read.csv("../output/twinstrand_simple_melt_merge.csv",header = T,stringsAsFactors = F)
# twinstrand_simple_melt_merge=read.csv("output/twinstrand_simple_melt_merge.csv",header = T,stringsAsFactors = F)

```

Formatting the data to have mutant and observed net growth rate
Also involves growth rate corrections
```{r}
twinstrand_simple_melt_merge=twinstrand_simple_melt_merge%>%
  mutate(drug_effect_obs=case_when(experiment=="M5"~drug_effect_obs+.015,
                                   experiment=="Enu_3"~drug_effect_obs-.011,
                                   experiment%in%c("M3","M6","M5","M4","M7")~drug_effect_obs)) #Therefore including both spike-in experiments and ENU mutagenized conditions.

```

Predicting clinical abundance using a glm around mutation bias and netgr

```{r}
#Using the mean of all experiments:
mean_netgr=twinstrand_simple_melt_merge%>%group_by(mutant)%>%summarize(netgr_mean=mean(netgr_obs,na.rm=T))

compicmut2=merge(compicmut,mean_netgr,by.x ="Compound",by.y="mutant")
# compicmut2$IC50=compicmut2$netgr
compicmut=compicmut2
#Notice that value here is your fitted IC50s
################Predictions using pooled IC50s################
fit5_pooled<-glm.nb(Abundance ~ netgr_mean+log10(Mutation.Probability), data=compicmut)
summary(fit5_pooled)

Data_fit=data.frame(cbind(compicmut,fit5_pooled$fitted.values)) ###Need to check that doing a cbind this way makes the right mutants go to the right row in compicmut. Pretty sure it does.
x=ggplot(data =Data_fit,aes(fit5_pooled.fitted.values,Abundance))
x+stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+geom_point(aes(size=1))+theme_classic()+theme(axis.text.x = element_text(size=15),axis.text.y = element_text(size=15))
# ggplot(compicmut,aes(x=IC50,y=(drug_effect_obs^.5),label=Compound))+geom_text()

################Predictions using individual IC50s################
fit5<-glm.nb(Abundance ~ IC50+log10(Mutation.Probability), data=compicmut) #Best 2 variable model
summary(fit5)
Data_fit=data.frame(cbind(Data_fit,fit5$fitted.values))
x=ggplot(data =Data_fit,aes(fit5.fitted.values,Abundance))
x+stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+geom_point(aes(size=1))+theme_classic()+theme(axis.text.x = element_text(size=15),axis.text.y = element_text(size=15))

#########Plotting predictions from inidivual IC50s and pooled experiments on the same plane#########
x=ggplot(data =Data_fit,aes(fit5.fitted.values,Abundance,label=Compound))
plotly=x+stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+geom_text(aes(size=1,color="blue"))+geom_text((aes(x=fit5_pooled.fitted.values,size=1.0,color="green")))+theme_classic()+theme(axis.text.x = element_text(size=15),axis.text.y = element_text(size=15))
ggplotly(plotly)

####Pearson's correlations
cor(Data_fit$fit5_pooled.fitted.values,Data_fit$Abundance,method="pearson")
cor(Data_fit$fit5.fitted.values,Data_fit$Abundance,method="pearson")
```

Predicting clinical abundances using the best spike-in mix
```{r}
#Using just the experiment that ended up giving us the best growth rates.
mean_netgr=twinstrand_simple_melt_merge%>%filter(experiment%in%c("M3"),duration%in%("d3d6"))
mean_netgr=mean_netgr%>%filter(!netgr_obs%in%NA)%>%
  dplyr::select(mutant,netgr_obs)



compicmut2=merge(compicmut,mean_netgr,by.x ="Compound",by.y="mutant")
# compicmut2$IC50=compicmut2$netgr
compicmut=compicmut2
#Notice that value here is your fitted IC50s
################Predictions using pooled IC50s################
# fit5_pooled<-glm.nb(Abundance ~ netgr_mean+(Mutation.Probability), data=compicmut)
# summary(fit5_pooled)
fit5_pooled<-glm.nb(Abundance ~ netgr_mean+log10(Mutation.Probability), data=compicmut)
############Adding the CIs of predictions and plotting################
# Could have used confint(fit5_pooled)
linkinv=family(fit5_pooled)$linkinv #Using the inverse link function. Whatever the fuck that means. Got it from here https://stackoverflow.com/questions/35235939/how-to-plot-logistic-glm-predicted-values-and-confidence-interval-in-r
pred=predict(fit5_pooled,newdata=compicmut,type="link", se.fit = T)

upper=linkinv(pred$fit)+(1.96*pred$se.fit)
lower=linkinv(pred$fit)-(1.96*pred$se.fit)

Data_fit=data.frame(cbind(compicmut,fit5_pooled$fitted.values)) ###Need to check that doing a cbind this way makes the right mutants go to the right row in compicmut. Pretty sure it does.
Data_fit=cbind(Data_fit,upper,lower)

x=ggplot(data =Data_fit,aes(fit5_pooled.fitted.values,Abundance))
x+stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+geom_point(aes(size=1))+theme_classic()+theme(axis.text.x = element_text(size=15),axis.text.y = element_text(size=15))
# ggplot(compicmut,aes(x=IC50,y=(drug_effect_obs^.5),label=Compound))+geom_text()
############Saving Predictions using pooled IC50s as a BMES figure################
x=ggplot(data =Data_fit,aes(Abundance,fit5_pooled.fitted.values))
x+geom_abline()+
  # stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+
  # geom_point(aes(size=1))+
  geom_point(aes(alpha=.7))+
  geom_errorbar(aes(ymin=lower,ymax=upper))+
  scale_y_continuous(name="Model Predicted Clinical Abundance",limits=c(0,42))+
  scale_x_continuous(name="Clinical Abundance",limits=c(0,42))+
  theme_classic()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15))+
  cleanup+
  theme(legend.position = "none")
###Coloring mutants by factor for Scott 5/28/21###
Data_fit$Compound=factor(Data_fit$Compound)
Data_fit$Compound=reorder(Data_fit$Compound,-Data_fit$Abundance)
Data_fit_simple=Data_fit%>%dplyr::select(Compound,IC50,Mutation.Probability,Abundance,Nuc_change,netgr_obs,Abundance_fit=fit5_pooled.fitted.values)
write.csv(Data_fit_simple,"clinicalabundance_predictions_pooled.csv")
x=ggplot(data =Data_fit,aes(Abundance,fit5_pooled.fitted.values,color=Compound))
x+geom_abline()+
  # stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+
  # geom_point(aes(size=1))+
  geom_point()+
  # geom_errorbar(aes(ymin=lower,ymax=upper))+
  scale_y_continuous(name="Model Predicted Clinical Abundance",limits=c(0,42))+
  scale_x_continuous(name="Clinical Abundance",limits=c(0,42))+
  theme_classic()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15))+
  cleanup+
  scale_color_manual(values=c(Palette("#FD0D39","#FF839E",19,mode="RGB",circular=F)))+
  theme(legend.position = "none")
###
ggsave("clinicalabundancepredictions_pooled_52821.pdf",width=3,height=3,units="in",useDingbats=F)
ggplot(data =Data_fit,aes(Abundance,fit5_pooled.fitted.values,label=Compound))+geom_abline()+
  geom_text()+
  cleanup
################Predictions using individual IC50s################
fit5<-glm.nb(Abundance ~ IC50+log10(Mutation.Probability), data=compicmut) #Best 2 variable model
summary(fit5)
Data_fit=data.frame(cbind(Data_fit,fit5$fitted.values))
x=ggplot(data =Data_fit,aes(fit5.fitted.values,Abundance))
x+stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+geom_point(aes(size=1))+theme_classic()+theme(axis.text.x = element_text(size=15),axis.text.y = element_text(size=15))

#########Plotting predictions from inidivual IC50s and pooled experiments on the same plane#########
x=ggplot(data =Data_fit,aes(fit5.fitted.values,Abundance,label=Compound))
plotly=x+stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+geom_text(aes(size=1,color="blue"))+geom_text((aes(x=fit5_pooled.fitted.values,size=1.0,color="green")))+theme_classic()+theme(axis.text.x = element_text(size=15),axis.text.y = element_text(size=15))
ggplotly(plotly)

####Pearson's correlations
cor(Data_fit$fit5_pooled.fitted.values,Data_fit$Abundance,method="pearson")
cor(Data_fit$fit5.fitted.values,Data_fit$Abundance,method="pearson")
```

Same chunk as above except that it makes a neat figure but the ic50 predictions rather than the pooled predictions
```{r}
#Using just the experiment that ended up giving us the best growth rates.
mean_netgr=twinstrand_simple_melt_merge%>%filter(experiment%in%c("M3"),duration%in%("d3d6"))
mean_netgr=mean_netgr%>%filter(!netgr_obs%in%NA)%>%
  dplyr::select(mutant,netgr_obs)



compicmut2=merge(compicmut,mean_netgr,by.x ="Compound",by.y="mutant")
# compicmut2$IC50=compicmut2$netgr
compicmut=compicmut2
#Notice that value here is your fitted IC50s
################Predictions using pooled IC50s################
# fit5_pooled<-glm.nb(Abundance ~ netgr_mean+(Mutation.Probability), data=compicmut)
# summary(fit5_pooled)
fit5_pooled<-glm.nb(Abundance ~ IC50+log10(Mutation.Probability), data=compicmut)
############Adding the CIs of predictions and plotting################
# Could have used confint(fit5_pooled)
linkinv=family(fit5_pooled)$linkinv #Using the inverse link function. Whatever the fuck that means. Got it from here https://stackoverflow.com/questions/35235939/how-to-plot-logistic-glm-predicted-values-and-confidence-interval-in-r
pred=predict(fit5_pooled,newdata=compicmut,type="link", se.fit = T)

upper=linkinv(pred$fit)+(1.96*pred$se.fit)
lower=linkinv(pred$fit)-(1.96*pred$se.fit)

Data_fit=data.frame(cbind(compicmut,fit5_pooled$fitted.values)) ###Need to check that doing a cbind this way makes the right mutants go to the right row in compicmut. Pretty sure it does.
Data_fit=cbind(Data_fit,upper,lower)

x=ggplot(data =Data_fit,aes(fit5_pooled.fitted.values,Abundance))
x+stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+geom_point(aes(size=1))+theme_classic()+theme(axis.text.x = element_text(size=15),axis.text.y = element_text(size=15))
# ggplot(compicmut,aes(x=IC50,y=(drug_effect_obs^.5),label=Compound))+geom_text()
############Saving Predictions using pooled IC50s as a BMES figure################
library("painter")
# library("ggplot2")
####Converting mutants to factors and ordering by abundance###
Data_fit$Compound=factor(Data_fit$Compound)
Data_fit$Compound=reorder(Data_fit$Compound,-Data_fit$Abundance)
###
x=ggplot(data =Data_fit,aes(Abundance,fit5_pooled.fitted.values))
x+geom_abline()+
  # stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+
  # geom_point(aes(size=1))+
  geom_point(aes(alpha=.7))+
  geom_errorbar(aes(ymin=lower,ymax=upper))+
  scale_y_continuous(name="Model Predicted Clinical Abundance",limits=c(0,42))+
  scale_x_continuous(name="Clinical Abundance",limits=c(0,42))+
  theme_classic()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15))+
  cleanup+
  theme(legend.position = "none")
# ggsave("clinicalabundancepredictions_ic50s_061020.pdf",width=2,height=2,units="in",useDingbats=F)
###Adding colors to plot for Scott 5/28/21
x=ggplot(data =Data_fit,aes(Abundance,fit5_pooled.fitted.values,color=(Compound)))
x+geom_abline()+
  # stat_function(fun=function(x)x, geom="line", aes(colour="square",size=1.0))+
  # geom_point(aes(size=1))+
  geom_point()+
  # geom_errorbar(aes(ymin=lower,ymax=upper))+
  scale_y_continuous(name="Model Predicted Clinical Abundance",limits=c(0,42))+
  scale_x_continuous(name="Clinical Abundance",limits=c(0,42))+
  theme_classic()+
  theme(axis.text.x = element_text(size=15),
        axis.text.y = element_text(size=15))+
  cleanup+
  scale_color_manual(values=c(Palette("#FD0D39","#FF839E",19,mode="RGB",circular=F)))+
  theme(legend.position = "none")
ggsave("clinicalabundancepredictions_ic50s_052821_v2.pdf",width=3,height=3,units="in",useDingbats=F)
###




ggplot(data =Data_fit,aes(Abundance,fit5_pooled.fitted.values,label=Compound))+geom_abline()+
  geom_text()+
  cleanup
```

Supplemental Analysis
```{r}
enu_plots=twinstrand_simple_melt_merge%>%filter(experiment%in%c("Enu_4","Enu_3"),duration%in%"d3d6")
#hardcoding adjustments to the growth rates
enu_plots$netgr_obs[enu_plots$experiment=="Enu_3"]=enu_plots$netgr_obs[enu_plots$experiment=="Enu_3"]-.011

a=twinstrand_simple_melt_merge%>%
  filter(!experiment%in%c("Enu_4","Enu_3"),duration%in%"d3d6",conc=="0.8")%>%
  mutate(netgr_obs=case_when(experiment=="M5"~netgr_obs+.015,
                                   experiment%in%c("M3","M6","M5","M4","M7")~netgr_obs))

a_sum=a%>%group_by(mutant,Spike_in_freq)%>%summarize(mean_netgr_pred=mean(netgr_pred),mean_netgr_obs=mean(netgr_obs),sd_netgr_obs=sd(netgr_obs),mean_drug_effect=mean(drug_effect_obs),sd_drug_effect=sd(drug_effect_obs),mean_drug_effect_pred=mean(drug_effect),sd_drug_effect_pred=sd(drug_effect))

plotly=ggplot(a_sum,aes(x=mean_netgr_pred,y=mean_netgr_obs,color=factor(Spike_in_freq)))+geom_errorbar(aes(ymin=mean_netgr_obs-sd_netgr_obs,ymax=mean_netgr_obs+sd_netgr_obs))+geom_point()+geom_point(data=enu_plots%>%filter(experiment%in%("Enu_3")),aes(x=netgr_pred,y=netgr_obs,color="red"))+geom_abline()+cleanup
ggplotly(plotly)

####Plotting drug effect on growth rate rather than net growth rate
plotly=ggplot(a_sum,aes(x=mean_drug_effect_pred,y=mean_drug_effect,color=factor(Spike_in_freq)))+geom_errorbar(aes(ymin=mean_drug_effect-sd_drug_effect,ymax=mean_drug_effect+sd_drug_effect))+geom_point()+geom_abline()+cleanup
ggplotly(plotly)

plotly=ggplot(a_sum%>%filter(!Spike_in_freq%in%c(5000)),aes(x=mean_drug_effect_pred,y=mean_drug_effect,color=factor(Spike_in_freq)))+geom_errorbar(aes(ymin=mean_drug_effect-sd_drug_effect,ymax=mean_drug_effect+sd_drug_effect))+geom_point()+geom_abline()+cleanup
ggplotly(plotly)


plotly=ggplot(a_sum,aes(x=mean_drug_effect_pred,y=mean_drug_effect,color=factor(mutant)))+geom_errorbar(aes(ymin=mean_drug_effect-sd_drug_effect,ymax=mean_drug_effect+sd_drug_effect))+geom_point()+geom_abline()+cleanup
ggplotly(plotly)
```

