---
title: "dose_response_curve_fitting"
author: "Haider Inam"
date: "6/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir=rprojroot::find_rstudio_root_file())
# rm(list=ls())
```

####Please change required directories this chunk if compiling in R rather than RmD
```{r}
#Inputs:
conc_for_predictions=0.8
net_gr_wodrug=0.055
#Reading required tables
# ic50data=read.csv("data/heatmap_concat_data.csv",header = T,stringsAsFactors = F)

ic50data=read.csv("/Users/haiderinam/Box/RProjects/duplex_sequencing_screen/data/heatmap_concat_data.csv",header = T,stringsAsFactors = F)
# ic50data=read.csv("../data/heatmap_concat_data.csv",header = T,stringsAsFactors = F)
```

```{r,include=F}
# rm(list=ls())
library(knitr)
library(tictoc)
library(workflowr)
library(VennDiagram)
library(dplyr)
library(foreach)
library(doParallel)
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(devtools)
library(ggsignif)
library(plotly)
library(BiocManager)
library(drc)
# library(ensembldb) #Loading this with Dplyr commands seems to throw an error in Rmd
# library(EnsDb.Hsapiens.v86) #Loading this with Dplyr commands seems to throw an error in Rmd

######################Cleanup for GGPlot2#########################################
cleanup=theme_bw() +
  theme(plot.title = element_text(hjust=.5),
        panel.grid.major = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(color = "black"),
        axis.text = element_text(face="bold",color="black",size="11"),
        text=element_text(size=11,face="bold"),
        axis.title=element_text(face="bold",size="11"))
```


##Data Parsing--  Dose Response Data  
###Importing model with BCR-ABL mutant dose responses (Chuan's data)
###Also applying the 2-parameter logistic. Upper and lower limits are fixed. May be good or bad.
```{r}
#Deciding not to use nls() because it's a pain in the ...
#https://www.youtube.com/watch?v=aXpJE7IGiPY this has a nice overview of curve fitting
# library(dplyr)
# rm(list=ls())
####Getting effect of drug on growth rate####

ic50data=ic50data[c(1:10),]
ic50data_long=melt(ic50data,id.vars = "conc",variable.name = "species",value.name = "y")
#Removing useless mutants (for example keeping only maxipreps and removing low growth rate mutants)
ic50data_long=ic50data_long%>%filter(species%in%c("Wt","V299L_H","E355A","D276G_maxi","H396R","F317L","F359I","E459K","G250E","F359C","F359V","M351T","L248V","E355G_maxi","Q252H_maxi","Y253F","F486S_maxi","H396P_maxi","E255K","Y253H","T315I","E255V"))



#Making standardized names
ic50data_long$mutant=ic50data_long$species
ic50data_long=ic50data_long%>%
  # filter(conc=="0.625")%>%
  # filter(conc=="1.25")%>%
  mutate(mutant=case_when(species=="F486S_maxi"~"F486S",
                          species=="H396P_maxi"~"H396P",
                          species=="Q252H_maxi"~"Q252H",
                          species=="E355G_maxi"~"E355G",
                          species=="D276G_maxi"~"D276G",
                          species=="V299L_H" ~ "V299L",
                          species==mutant ~as.character(mutant)))

# ic50data_long_625$species[order((ic50data_long_625$y),decreasing = T)]

#In the next step, I'm ordering mutants by decreasing resposne to the 625nM dose. Then I use this to change the levels of the species factor from more to less resistant. This helps with ggplot because now I can color the mutants with decreasing resistance
ic50data_long_625=ic50data_long%>%filter(conc==.625)
ic50data_long$species=factor(ic50data_long$species,levels = as.character(ic50data_long_625$species[order((ic50data_long_625$y),decreasing = T)]))

#Plotting the normalized dose response curves
getPalette = colorRampPalette(brewer.pal(9, "Spectral"))

plotly=ggplot(ic50data_long,aes(x=conc,y=y,color=factor(species)))+
  facet_wrap(~factor(species))+
  # geom_line()+
  geom_point()+
  cleanup+
  scale_x_continuous(trans="log10")+
  scale_color_manual(values = getPalette(length(unique(ic50data_long$species))))

ggplotly(plotly)
```
###Dose response curve fitting with 4-parameter logistic
####First iteration: Have a y_model for only the drug concentrations Chuan used
Essentially, all this is doing is adding a column for y-model to IC50data_long. Default was just y (proportion alive).
```{r}
########Four parameter logistic########
#Reference: https://journals.plos.org/plosone/article/file?type=supplementary&id=info:doi/10.1371/journal.pone.0146021.s001
#In short: For each dose in each species, get the response
# rm(list=ls())
ic50data_long_model=data.frame()
for (species_curr in sort(unique(ic50data_long$species))){
  ic50data_species_specific=ic50data_long%>%filter(species==species_curr)
  x=ic50data_species_specific$conc
  y=ic50data_species_specific$y
  #Next: Appproximating Response from dose (inverse of the prediction)
  ic50.ll4=drm(y~conc,data=ic50data_long%>%filter(species==species_curr),fct=LL.3(fixed=c(NA,1,NA)))
    b=coef(ic50.ll4)[1]
    c=0
    d=1
    e=coef(ic50.ll4)[2]
  ###Getting predictions
  ic50data_species_specific=ic50data_species_specific%>%group_by(conc)%>%mutate(y_model=c+((d-c)/(1+exp(b*(log(conc)-log(e))))))
  ic50data_species_specific=data.frame(ic50data_species_specific) #idk why I have to end up doing this
  ic50data_long_model=rbind(ic50data_long_model,ic50data_species_specific)
}
ic50data_long=ic50data_long_model

#In the next step, I'm ordering mutants by decreasing resposne to the 625nM dose. Then I use this to change the levels of the species factor from more to less resistant. This helps with ggplot because now I can color the mutants with decreasing resistance
ic50data_long_625=ic50data_long%>%filter(conc==.625)
ic50data_long$species=factor(ic50data_long$species,levels = as.character(ic50data_long_625$species[order((ic50data_long_625$y_model),decreasing = T)]))

#Adding drug effect
##########Changed this on 2/20. Using y from 4 parameter logistic rather than raw values
ic50data_long=ic50data_long%>%
  # filter(!species=="Wt")%>%
  mutate(drug_effect=-log(y_model)/72)
# write.csv(ic50data_long,"ic50_growthratepredictions_forIvan.csv")
#Adding Net growth rate
ic50data_long$netgr_pred=net_gr_wodrug-ic50data_long$drug_effect
```
####Plotting modeled dose responses  
```{r}
getPalette = colorRampPalette(brewer.pal(9, "Spectral"))
plotly=ggplot(ic50data_long,aes(x=conc,color=factor(species)))+
  facet_wrap(~factor(species))+
  geom_line(aes(y=y_model))+
  geom_point(aes(y=y))+
  cleanup+
  scale_x_continuous(trans="log10")+
  scale_color_manual(values = getPalette(length(unique(ic50data_long$species))))
ggplotly(plotly)
```
Here I'm going to plot dose-responses with actual data and predicted data
```{r}

```

####Plotting species changes in dose responses over different concentrations  
```{r}
plotly=ggplot(ic50data_long,aes(x=species,y=y_model))+
  facet_wrap(~factor(conc))+
  geom_col(aes(fill=factor(species)))+
  cleanup+
  scale_fill_manual(values = getPalette(length(unique(ic50data_long$species))))+
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())
ggplotly(plotly)
```


###Dose response curve fitting with 4-parameter logistic
####Second iteration: Get y_model for predefined concentration ranges of interest
```{r}
conc.list=seq(.2,10,by=.1)
ic50.model.pred=data.frame(matrix(NA,nrow=length(conc.list)*length(unique(ic50data_long$species)),ncol=0))
for(species_curr in sort(unique(ic50data_long$mutant))){
  ic50data_species_specific=ic50data_long%>%filter(mutant==species_curr)
  #Next: Appproximating Response from dose (inverse of the prediction)
  ic50.ll4=drm(y~conc,data=ic50data_species_specific,fct=LL.3(fixed=c(NA,1,NA)))
  #Extracting coefficients
  b=coef(ic50.ll4)[1]
  c=0
  d=1
  e=coef(ic50.ll4)[2]
  rm(ic50.model.pred.species.specific)
  ic50.model.pred.species.specific=data.frame(matrix(NA,nrow=length(conc.list),ncol=0))
  i=1
  ic50.model.pred.species.specific$mutant=species_curr
  #For loop for the unique concentrations
  for(conc.curr in conc.list){
    ic50.model.pred.species.specific$conc[i]=conc.curr
    ic50.model.pred.species.specific$y_model[i]=c+((d-c)/(1+exp(b*(log(conc.curr)-log(e)))))
    i=i+1
  }
  ic50.model.pred=rbind(ic50.model.pred,ic50.model.pred.species.specific)
}
#Adding drug effect
ic50.model.pred=ic50.model.pred%>%
  # filter(!mutant=="Wt")%>%
  mutate(drug_effect=-log(y_model)/72)

    #Adding Net growth rate
    # ic50.model.pred$netgr_pred=.055-ic50.model.pred$drug_effect
ic50data_long=ic50.model.pred
ic50data_all_conc=ic50data_long
```



####Changing the format of the IC50s dataframe so that it matches twinstrand data labeling etc  
####Also converting dose response to expected change in growth rate
####This requires estimating a growth rate without drug. Note that I am using k=0.055 or 14 hours right now.
```{r}
#Variables when making predictions:
#Your assumed fitness without drug
ic50data_long$netgr_pred=net_gr_wodrug-ic50data_long$drug_effect
#Your assumed concentration
ic50data_long=ic50data_long%>%filter(conc==conc_for_predictions) ###Can remove this filter if you wanna look at how well predictions would match up if there was a systematic difference in the concentrations Chuan used and you used in your IC50s
    ##########Changed this on 2/20. Using y from 4 parameter logistic rather than raw values
# ic50data_formerge=ic50data_long%>%filter(!species=="Wt")%>%mutate(drug_effect=-log(y)/72)
# ic50data_formerge=ic50data_long%>%filter(!species=="Wt")%>%mutate(drug_effect=-log(y_model)/72)
```

```{r}
head(ic50data_all_conc)
# write.csv(ic50data_all_conc,"ic50data_all_conc.csv")
```

Next, I'm going to look a little closely at the errors we typically see in dose response curves:
```{r}

```

Below, I'm going to plot dose response curves with errorbars representing real day to day variation. 
```{r}
ic50heatmap=read.csv("data/IC50HeatMap.csv")
# a=ic50heatmap%>%mutate(mutant=species)%>%dplyr::select(!species)
# b=a%>%group_by(mutant)%>%rowwise()%>%summarize(replicate=n())
ic50heatmap=ic50heatmap%>%mutate(mutant=species)%>%dplyr::select(!species)
ic50heatmap=ic50heatmap%>%filter(mutant%in%c("V299L_H","E355A","D276G_maxi","H396R","F317L","F359I","E459K","G250E","F359C","F359V","M351T","L248V","E355G_maxi","Q252H_maxi","Y253F","F486S_maxi","H396P_maxi","E255K","Y253H","T315I","E255V","WT"))
ic50heatmap=ic50heatmap%>%
  mutate(mutant=case_when(mutant=="F486S_maxi"~"F486S",
                          mutant=="H396P_maxi"~"H396P",
                          mutant=="Q252H_maxi"~"Q252H",
                          mutant=="E355G_maxi"~"E355G",
                          mutant=="D276G_maxi"~"D276G",
                          mutant=="WT"~"Wt",
                          TRUE~mutant))

ic50heatmap_melt=melt(ic50heatmap,"mutant",variable.name = "conc",value.name = "y")
ic50heatmap_melt$conc=as.character(ic50heatmap_melt$conc)
ic50heatmap_melt=ic50heatmap_melt%>%filter(!conc%in%"Vehicle")
ic50heatmap_melt=ic50heatmap_melt%>%rowwise()%>%mutate(conc=as.numeric(as.character(strsplit(conc,"X")[[1]][2])))
ic50heatmap_sd=ic50heatmap_melt%>%
  group_by(mutant,conc)%>%
  summarize(y_mean=mean(y),y_sd=sd(y),y_n=n())%>%
  mutate(y_se=y_sd/sqrt(y_n),y_ci=qt(1-(.05/2),y_n-1)*y_se)

ic50data_long=read.csv("output/ic50data_all_conc.csv",header = T,stringsAsFactors = F,row.names = 1)
# ic50heatmap_sd$mutant=factor(ic50heatmap_sd$mutant,levels = as.character(unique(ic50heatmap_sd$mutant[order((ic50heatmap_sd$netgr_pred_mean),decreasing = T)])))
ic50data_long_625=ic50data_long%>%filter(conc==.6)
ic50data_long$mutant=factor(ic50data_long$mutant,levels = as.character(ic50data_long_625$mutant[order((ic50data_long_625$y),decreasing = T)]))
ic50heatmap_sd$mutant=factor(ic50heatmap_sd$mutant,levels = as.character(ic50data_long_625$mutant[order((ic50data_long_625$y),decreasing = T)]))

getPalette = colorRampPalette(brewer.pal(9, "Spectral"))
ggplot(ic50heatmap_sd%>%filter(conc>=.1,!mutant%in%c("F486S","F359C","E355A","D276G","V299L","Wt")),aes(x=conc,y=y_mean))+
  geom_point(color="black",size=2,shape=21,aes(fill=mutant))+
  geom_errorbar(aes(ymin=y_mean-y_sd,ymax=y_mean+y_sd,width=.1))+
  scale_x_continuous(name="Dose (uM)",trans="log10")+
  scale_y_continuous(name="Response")+
  cleanup+
  geom_line(data=ic50data_long%>%filter(!mutant%in%c("F486S","F359C","E355A","D276G","V299L","Wt")),aes(x=conc,y=y_model),linetype="dashed")+
  scale_fill_manual(values =getPalette(length(unique(ic50data_long$mutant))))+
  theme(legend.position = "none",axis.text =
          element_text(size=9,color="black",face="plain"),axis.title =
          element_text(size=10,color="black",face="bold"),
        strip.text = element_blank(),
        axis.text.x = element_text(angle=90,hjust=.5,vjust=.5))+
  facet_wrap(~mutant)
# ggsave("allmuts_dose_response.pdf",width=4,height=4,units="in",useDingbats=F)


ggplot(ic50heatmap_sd%>%filter(mutant%in%"E255K",conc>=.1),aes(x=conc,y=y_mean))+geom_point(color="black",size=3,shape=21,aes(fill="green"))+geom_errorbar(aes(ymin=y_mean-y_sd,ymax=y_mean+y_sd,width=.1))+scale_x_continuous(name="Dose (uM)",trans="log10")+scale_y_continuous(name="Response")+cleanup+geom_vline(aes(xintercept=.625),linetype="dashed")+geom_line(data=ic50data_long%>%filter(mutant%in%"E255K"),aes(x=conc,y=y_model))+scale_fill_manual(values = "#1CCE16")+theme(legend.position = "none",axis.text = element_text(size=9,color="black",face="plain"),axis.title = element_text(size=10,color="black",face="bold"))
# ggsave("e255k_dose_response.pdf",width=2,height=2,units="in",useDingbats=F)


ggplot(ic50heatmap_sd%>%filter(mutant%in%"Wt",conc>=.1),aes(x=conc,y=y_mean))+geom_point(color="black",size=3,shape=21,aes(fill="green"))+geom_errorbar(aes(ymin=y_mean-y_sd,ymax=y_mean+y_sd,width=.1))+scale_x_continuous(name="Dose (uM)",trans="log10")+scale_y_continuous(name="Response")+cleanup+geom_vline(aes(xintercept=.625),linetype="dashed")+geom_line(data=ic50data_long%>%filter(mutant%in%"Wt"),aes(x=conc,y=y_model))+scale_fill_manual(values = "#5941A9")+theme(legend.position = "none",axis.text = element_text(size=9,color="black",face="plain"),axis.title = element_text(size=10,color="black",face="bold"))
# ggsave("bcrablwt_dose_response.pdf",width=2,height=2,units="in",useDingbats=F)
# write.csv(ic50heatmap_sd,"output/ic50heatmap_sd_ci.csv")
```

```{r}
################Looking at the typical error in dose-response#######
plotly=ggplot(ic50heatmap_sd%>%filter(conc%in%.625),aes(x=mutant,y=y_mean))+geom_point()+geom_errorbar(aes(ymin=y_mean-y_sd,ymax=y_mean+y_sd))
ggplotly(plotly)

Wt=ic50heatmap_sd%>%filter(mutant%in%"Wt")
conc=Wt$conc

ic50.ll4=drm(y_mean~conc,data=ic50heatmap_sd%>%filter(mutant%in%"Wt"),fct=LL.3(fixed=c(NA,1,NA)))
    b=coef(ic50.ll4)[1]
    c=0
    d=1
    e=coef(ic50.ll4)[2]

###Getting predictions
Wt=Wt%>%group_by(conc)%>%mutate(y_model=c+((d-c)/(1+exp(b*(log(conc)-log(e))))))

predict(ic50.ll4,data.frame(dose=.625))
###We saw that at 625nM, Wt has a mean dose response of .03 with a standard deviation of .011 (range of .0195 to .0405)
predict(ic50.ll4,data.frame(dose=1.62))
predict(ic50.ll4,data.frame(dose=1.05))
predict(ic50.ll4,data.frame(dose=1.25))
#Therefore the typical error in dose-response for a dose of 1.25 goes from 1.05 to 1.62

```

