---
title: "DupSeq_QC_Lane11"
author: "Haider Inam"
date: '2022-08-22'
output: html_document
---

```{r setup, include=FALSE}
# rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath(".."))

library(stringr)
library(dplyr)
library(ggplot2)
library(plotly)
library(tictoc)
library(doParallel)
library(foreach)
#Cleanup code for plotting
cleanup=theme_bw() +
  theme(plot.title = element_text(hjust=.5),
        panel.grid.major = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(color = "black"),
        axis.text = element_text(face="bold",color="black",size="11"),
        text=element_text(size=11,face="bold"),
        axis.title=element_text(face="bold",size="11"))
```

In the following chunks, I'm going to be doing some QC with the duplex sequencing data from novogene lane 11
This sequencing run had both EGFR and ABL data. The libraries are twist libraries.

I'm going to be looking closely at the following:  
* Count distributions of EGFR vs ABL
* How much coverage do we get with a single sample of EGFR vs with two samples?
  Answer: 100k for 1 sample, 200k for two SSCS samples
* What is the % on-target?
* What is the % N?
* What is the % of split reads?
* What is the % mouse?

* How much coverage do we get for DCS vs for SSCS?
  Answer: For a dupseq coverage of 40k, our SSCS coverage was 100k
  This is a very low % of SSCS reads that are orphaned. For schmitt's adapter types, about 80-90% of the SSCS reads are orphaned.
* What is the error rate for SSCS vs for DCS?
  Answer:
* What is the % of mouse reads that we're seeing for the samples?
  Answer: Mouse read %age is very low for EGFR (1% of the barcodes align to the mouse genome). For ABL, between 1 and 30% of the consensus reads align to the mouse genome
* How many unique mutants do we see for EGFR? What percent coverage is that?
  Answer: Combining two EGFR samples at the baseline and using SSCS counts, we achieve a coverage of 200k. At this coverage, we're seeing 2340 out of 2700 mutants that twist's QC data saw. That's 90% of the mutants at baseline.
* What is the count distribution of the mutants in the data? aka how many times do we see each mutant?
  Answer:
* How many unique mutants do you see per 10k barcodes sequenced? How does downsampling influence the sequencing data output?
  Answer: 
* How well do the mutant allele frequencies agree with twist's MAFs?
* How many reads/consensus barcodes are taken up by each of the residues?
* What percent of the barcodes are taken up by the top 10 mutants? What about the top 50 mutants?
* Modify the function so that you're not relying on ensembl's VEP. 

Sample 6
```{r}
# sample5_all=read.csv("data/Consensus_Data/Novogene_lane11/sample5/variants_ann_sample5.csv")
sample5_sum=read.csv("data/Consensus_Data/Novogene_lane11/sample5/variants_unique_ann_sample5.csv")
# sample5_all=read.csv("data/Consensus_Data/Novogene_lane11/sample5/variants_ann_sample5.csv")
# a=sample5_all%>%filter(protein_start%in%903,ref%in%"T",alt%in%"C")

sample6_all=read.csv("data/Consensus_Data/Novogene_lane11/sample6/variants_ann_sample5&6.csv")
sample6_sum=read.csv("data/Consensus_Data/Novogene_lane11/sample6/variants_unique_ann.csv")
sample5_simple=sample5_sum%>%dplyr::select(alt_start_pos,protein_start,ref,alt,consequence_terms,amino_acids,ct,depth)
sample5_simple$sample="sample5"
sample6_simple=sample6_sum%>%dplyr::select(alt_start_pos,protein_start,ref,alt,consequence_terms,amino_acids,ct,depth)
sample6_simple$sample="sample6"
sample56=rbind(sample5_simple,sample6_simple)
# a=sample56%>%filter(protein_start>=715,protein_start<=900,consequence_terms%in%"missense_variant")
plotly=ggplot(sample56%>%filter(protein_start>=715,protein_start<=900,consequence_terms%in%"missense_variant"),aes(x=protein_start,y=depth,fill=sample))+geom_col(position=position_dodge())+facet_wrap(~sample)+cleanup
ggplotly(plotly)
```
```{r}
sample56_merged=merge(sample5_simple,sample6_simple,by=c("alt_start_pos","protein_start","ref","alt","consequence_terms","amino_acids"),all.x = T)

# a=sample56_merged%>%filter(depth.x>=1000,protein_start>=715,protein_start<=870,consequence_terms%in%"missense_variant")
sample56_merged[sample56_merged$ct.y%in%NA,10]=1000
sample56_merged[sample56_merged$depth.y%in%NA,11]=1000
# sample56_merged=sample56_merged%>%
#   rowwise()%>%
#   mutate(ct.y=case_when(ct.y%in%NA~0,
#                         T~ct.y))
ggplot(sample56_merged%>%filter(depth.x>=1000,protein_start>=715,protein_start<=870,consequence_terms%in%"missense_variant"),aes(x=ct.x/depth.x,y=ct.y/depth.y))+
  geom_point(color="black",shape=21,aes(fill=log10(ct.x)))+
  scale_x_continuous(trans="log10")+
  scale_y_continuous(trans="log10")+
  cleanup


plotly=ggplot(sample5_sum%>%filter(protein_start>=715,protein_start<=870,consequence_terms%in%"missense_variant",ct<=50,type%in%"mnv"),aes(x=ct))+
  geom_histogram(aes(y=..density..),color=1,fill="white",bins=50)+
  geom_density(lwd = 1, colour = 4,fill = 4, alpha = 0.25)
ggplotly(plotly)

plotly=ggplot(sample6_sum%>%filter(protein_start>=715,protein_start<=870,consequence_terms%in%"missense_variant",ct<=50,type%in%"mnv"),aes(x=ct))+
  geom_histogram(aes(y=..density..),color=1,fill="white",bins=50)+
  geom_density(lwd = 1, colour = 4,fill = 4, alpha = 0.25)
  # scale_x_continuous(trans="log10")
ggplotly(plotly)


a=sample5_sum%>%filter(protein_start>=715,protein_start<=870,consequence_terms%in%"missense_variant",ct==1)
nrow(a%>%filter(type%in%"mnv"))
b=sample6_sum%>%filter(protein_start>=715,protein_start<=870,consequence_terms%in%"missense_variant",ct==1)
nrow(b%>%filter(type%in%"mnv"))
#For sample 5, out of the mutants that are only seen once, 34% are mnvs (a lot of SNP errors). So a lot of the mutants that we are seeing at a coverage of 1 are false. This means that for sample 5, the distribution of mutants is centered >1
#For sample 6, out of the mutants that are only seen once, 62% are mnvs (low SNP errors)

calls_sum=sample5_sum%>%filter(consequence_terms%in%"missense_variant")%>%group_by(protein_start)%>%summarize(unique_mutants=n(),count=sum(ct))
ggplot(calls_sum%>%filter(protein_start>=715,protein_start<=870),aes(x=protein_start,y=unique_mutants))+geom_col()+cleanup

ggplot(calls_sum%>%filter(protein_start>=715,protein_start<=870),aes(x=protein_start,y=count))+geom_col()+cleanup


calls_sum=sample6_sum%>%filter(consequence_terms%in%"missense_variant")%>%group_by(protein_start)%>%summarize(unique_mutants=n(),count=sum(ct))
ggplot(calls_sum%>%filter(protein_start>=715,protein_start<=870),aes(x=protein_start,y=unique_mutants))+geom_col()+cleanup

ggplot(calls_sum%>%filter(protein_start>=715,protein_start<=870),aes(x=protein_start,y=count))+geom_col()+cleanup
ggplot(calls_sum%>%filter(protein_start>=715,protein_start<=870,!protein_start%in%861),aes(x=protein_start,y=count))+geom_col()+cleanup
ggplot(calls_sum%>%filter(protein_start>=715,protein_start<=870,!protein_start%in%c(861,791)),aes(x=protein_start,y=count))+geom_col()+cleanup
# a=sample5_sum%>%filter(consequence_terms%in%"missense_variant",protein_start>=715,protein_start<=870)
# sum(a$ct)

```



Sample 6
```{r}
calls_missense=calls_missense%>%
  filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])

ggplot(calls_missense,aes(x=protein_start,y=alt_aa))+
  geom_tile(color="black",aes(fill=(ct/depth)))+
  scale_x_continuous(name="Position along EGFR Kinase",expand=c(0,0),limits=c(717,870))+
  scale_y_discrete(name="Amino Acid Substitution",expand=c(0,0))+
  scale_fill_continuous(name="Allele \nFrequency",trans="log10")+
  cleanup+
  theme(legend.position = "none")
# a=calls_missense%>%filter(protein_start>=715,protein_start<=880)
# ggsave("egfr_heatmap_sample5.pdf",width=6,height=4,units = "in",useDingbats=F)

ggplot(calls_missense_sum,aes(x=protein_start,y=count))+geom_col()+scale_x_continuous(limits=c(710,875))
```


SAMPLE 2
```{r,eval=F}
library("plotly")
sample2_sum=read.csv("data/Consensus_Data/Novogene_lane11/sample2/sscs_sum_ann.csv",header = T,stringsAsFactors = F)[-1]
sample2_sum$consensus="sscs"
sample2_sum=sample2_sum%>%
  # filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])

sample2_all=read.csv("data/Consensus_Data/Novogene_lane11/sample2/sscs_reads_ann.csv",header = T,stringsAsFactors = F)[-1]
sample2_all$consensus="sscs"
# dcs_sum=read.csv("data/Consensus_Data/Novogene_lane11/sample2/duplex_sum_ann.csv",header = T,stringsAsFactors = F)[-1]
# dcs_sum$consensus="dcs"

sample2_all=sample2_all%>%
  # filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])
a=sample2_all%>%filter(protein_start%in%493,amino_acids%in%"F")

sample2_sum

dcs_sum=dcs_sum%>%
  filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])

ggplot(sample2_sum,aes(x=protein_start,y=alt_aa))+
  geom_tile(color="black",aes(fill=ct))+
  scale_x_continuous(expand=c(0,0),limits=c(242,333))+
  scale_y_discrete(expand=c(0,0))

all_sum=rbind(sample2_sum,dcs_sum)

plotly=ggplot(all_sum,aes(x=ct,fill=consensus,alpha=0.5))+
  geom_density(position=position_dodge(),bins=100)+
  scale_x_continuous(limits=c(0,100))
  # scale_x_continuous(trans="log10")
ggplotly(plotly)

plotly=ggplot(all_sum,aes(x=ct,fill=consensus,alpha=0.5))+
  geom_density(position=position_dodge(),bins=100)+
  # scale_x_continuous(limits=c(0,100))+
  scale_x_continuous(trans="log10")
ggplotly(plotly)



ggplot(all_sum,aes(x=protein_start,y=alt_aa))+
  geom_tile(color="black",aes(fill=ct))+
  facet_grid(~consensus)+
  scale_x_continuous(expand=c(0,0),limits=c(241,333))+
  scale_y_discrete(expand=c(0,0))+
  scale_fill_gradient(na.value = "black",low="red",high="blue",name="Count")a

a=sscs_sum%>%filter(protein_start>=242,protein_start<=289)
a=a%>%group_by(protein_start)%>%summarize(count=n())

calls_sum=sample2_sum%>%filter(consequence_terms%in%"missense_variant")%>%group_by(protein_start)%>%summarize(unique_mutants=n(),count=sum(ct))

ggplot(calls_sum%>%filter(protein_start>=242,protein_start<=500),aes(x=protein_start,y=count))+geom_col()+cleanup
ggplot(calls_sum%>%filter(protein_start>=242,protein_start<=500),aes(x=protein_start,y=unique_mutants))+geom_col()+cleanup

a=sample2_sum%>%filter(consequence_terms%in%"missense_variant",protein_start>=242,protein_start<=500)
sum(a$ct)
```
SAMPLE 10 and 11
```{r,eval=F}
###########Sample 10############
sscs_sum=read.csv("Novogene_lane11/sample10/sscs_sum_ann.csv",header = T,stringsAsFactors = F)[-1]

sscs_sum=sscs_sum%>%
  filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])

ggplot(sscs_sum,aes(x=protein_start,y=alt_aa))+
  geom_tile(color="black",aes(fill=ct))+
  scale_x_continuous(expand=c(0,0),limits=c(242,330))+
  scale_y_discrete(expand=c(0,0))

###########Sample 8############
sscs_sum=read.csv("Novogene_lane11/sample8/sscs_sum_ann.csv",header = T,stringsAsFactors = F)[-1]

sscs_sum=sscs_sum%>%
  filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])

ggplot(sscs_sum,aes(x=protein_start,y=alt_aa))+
  geom_tile(color="black",aes(fill=ct))+
  scale_x_continuous(expand=c(0,0),limits=c(242,330))+
  scale_y_discrete(expand=c(0,0))
```

SAMPLE 7
```{r,eval=F}
###########Sample 10############
sscs_sum=read.csv("Novogene_lane11/sample7/sscs_sum_ann.csv",header = T,stringsAsFactors = F)[-1]

sscs_sum=sscs_sum%>%
  filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])

ggplot(sscs_sum,aes(x=protein_start,y=alt_aa))+
  geom_tile(color="black",aes(fill=ct))+
  # scale_x_continuous(expand=c(0,0),limits=c(242,330))+
  scale_x_continuous(expand=c(0,0))+
  scale_y_discrete(expand=c(0,0))

###########Sample 8############
sscs_sum=read.csv("Novogene_lane11/sample8/sscs_sum_ann.csv",header = T,stringsAsFactors = F)[-1]

sscs_sum=sscs_sum%>%
  filter(protein_start==protein_end,consequence_terms%in%"missense_variant")%>%
  rowwise()%>%
  mutate(ref_aa=strsplit(amino_acids,"/")[[1]][1],
         alt_aa=strsplit(amino_acids,"/")[[1]][2])

ggplot(sscs_sum,aes(x=protein_start,y=alt_aa))+
  geom_tile(color="black",aes(fill=ct))+
  scale_x_continuous(expand=c(0,0),limits=c(242,330))+
  scale_y_discrete(expand=c(0,0))
```
