---
title: "growthrate_plots_ENU"
author: "Haider Inam"
date: "4/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

####Please change required directories this chunk if compiling in R rather than RmD
```{r}
#Inputs:
conc_for_predictions=0.8
net_gr_wodrug=0.05
#Reading required tables
# twinstrand_maf_merge=read.csv("../output/twinstrand_maf_merge.csv",header = T,stringsAsFactors = F)
twinstrand_maf_merge=read.csv("output/twinstrand_maf_merge.csv",header = T,stringsAsFactors = F)

# twinstrand_simple_melt_merge=read.csv("../output/twinstrand_simple_melt_merge.csv",header = T,stringsAsFactors = F)
twinstrand_simple_melt_merge=read.csv("output/twinstrand_simple_melt_merge.csv",header = T,stringsAsFactors = F)
```

```{r,include=F}
# rm(list=ls())
library(knitr)
library(tictoc)
library(workflowr)
library(VennDiagram)
library(dplyr)
library(foreach)
library(doParallel)
library(ggplot2)
library(reshape2)
library(RColorBrewer)
library(devtools)
library(ggsignif)
library(plotly)
library(BiocManager)
library(drc)
# library(ensembldb) #Loading this with Dplyr commands seems to throw an error in Rmd
# library(EnsDb.Hsapiens.v86) #Loading this with Dplyr commands seems to throw an error in Rmd

######################Cleanup for GGPlot2#########################################
cleanup=theme_bw() +
  theme(plot.title = element_text(hjust=.5),
        panel.grid.major = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(color = "black"),
        axis.text = element_text(face="bold",color="black",size="11"),
        text=element_text(size=11,face="bold"),
        axis.title=element_text(face="bold",size="11"))
```


####Looking at the required depth for ENU
####Seeing if the non-model, raw IC50s match observed dose response in data better
####Plot mean of the distributions for expected vs observed IC50s
Changes I've made so far: added annotations for the mutants that we didn't otherwise see in the normal data. Added some annodations for the ENU experiment time point and spike in frequencies.
```{r}
# ###In this section, all I'm doing is importing the twinstrand_maf_merge dataframe and annotating mutants. This is essentially copied over from the sections above but is present in the same chunks so that I don't have to go looking at chunks...
# twinstrand_maf=read.table("Twinstrand/prj00053-2019-12-02.deliverables/all.mut",sep="\t",header = T,stringsAsFactors = F)
# names=read.table("Twinstrand/prj00053-2019-12-02.deliverables/manifest.tsv",sep="\t",header = T,stringsAsFactors = F)
# twinstrand_maf_merge=merge(twinstrand_maf,names,by.x = "Sample",by.y = "TwinstrandId")
# ###These mutations include the mutations found in the normal data and ALSO mutants found only in the ENU data
# twinstrand_maf_merge=twinstrand_maf_merge%>%
#   mutate(mutant=case_when(End==130872896 & ALT=="T" ~ "T315I",
#                           End==130862970 & ALT=="C" ~ "Y253H",
#                           End==130862977 & ALT=="T" ~ "E255V",
#                           End==130873004 & ALT=="C" ~ "M351T",
#                           End==130862962 & ALT=="A" ~ "G250E",
#                           End==130874969 & ALT=="C" ~ "H396P",
#                           End==130862955 & ALT=="G" ~ "L248V",
#                           End==130874969 & ALT=="G" ~ "H396R",
#                           End==130862971 & ALT=="T" ~ "Y253F",
#                           End==130862969 & ALT=="T" ~ "Q252H",
#                           End==130862976 & ALT=="A" ~ "E255K",
#                           End==130872901 & ALT=="C" ~ "F317L",
#                           End==130873027 & ALT=="C" ~ "F359L",
#                           End==130873027 & ALT=="G" ~ "F359V",
#                           End==130873027 & ALT=="A" ~ "F359I",
#                           End==130873016 & ALT=="G" ~ "E355G",
#                           End==130873016 & ALT=="C" ~ "E355A",
#                           End==130878519 & ALT=="A" ~ "E459K",
#                           End==130872911 & ALT=="G" ~ "Y320C",
#                           End==130872133 & ALT=="G" ~ "D276G",
#                           End==130862969 & ALT=="C" ~ "Q252H", ###The mutants below were found only in the ENU mutagenized pools
#                           End==130872885 & ALT=="G" ~ "F311L",
#                           End==130873028 & ALT=="G" ~ "F359C",
#                           End==130874971 & ALT=="C" ~ "A397P",
#                           End==130862854 & ALT=="G" ~ "H214R",
#                           End==130872146 & ALT=="C" ~ "V280syn",
#                           End==130872161 & ALT=="T" ~ "K285N",
#                           End==130872923 & ALT=="G" ~ "L324R",
#                           End==130872983 & ALT=="T" ~ "A344D"))
# 
# twinstrand_maf_merge$totalcells=0
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M3"&twinstrand_maf_merge$time_point=="D0"]=493000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M3"&twinstrand_maf_merge$time_point=="D3"]=1295000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M3"&twinstrand_maf_merge$time_point=="D6"]=13600000
# ##########M5##########
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M5"&twinstrand_maf_merge$time_point=="D0"]=588000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M5"&twinstrand_maf_merge$time_point=="D3"]=1299000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M5"&twinstrand_maf_merge$time_point=="D6"]=11294000
# ##########M7##########
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M7"&twinstrand_maf_merge$time_point=="D0"]=611000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M7"&twinstrand_maf_merge$time_point=="D3"]=857000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M7"&twinstrand_maf_merge$time_point=="D6"]=14568000
# ##########M4##########
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M4"&twinstrand_maf_merge$time_point=="D0"]=405000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M4"&twinstrand_maf_merge$time_point=="D3"]=980000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M4"&twinstrand_maf_merge$time_point=="D6"]=1783000
# ##########M6##########
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M6"&twinstrand_maf_merge$time_point=="D0"]=510000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M6"&twinstrand_maf_merge$time_point=="D3"]=798000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="M6"&twinstrand_maf_merge$time_point=="D6"]=842000
# ##########ENU3##########
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="Enu_3"&twinstrand_maf_merge$time_point=="D0"]=166000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="Enu_3"&twinstrand_maf_merge$time_point=="D3"]=1282000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="Enu_3"&twinstrand_maf_merge$time_point=="D6"]=97200000
# ##########ENU4##########
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="Enu_4"&twinstrand_maf_merge$time_point=="D0"]=316000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="Enu_4"&twinstrand_maf_merge$time_point=="D3"]=1264000
# twinstrand_maf_merge$totalcells[twinstrand_maf_merge$experiment=="Enu_4"&twinstrand_maf_merge$time_point=="D6"]=40000000
# 
# 
# # a=twinstrand_maf_merge%>%select(Annotation,CustomerName,experiment,REF,ALT,Depth,AltDepth,mutant,time_point)%>%filter(grepl("ENU",Annotation,ignore.case = T),time_point%in%c("D0","D3","D6"))%>%arrange(desc(AltDepth))
# 
# 
# 
# #Adding columns for experiment names, experiment frequencies, and time
# twinstrand_maf_merge$experiment[twinstrand_maf_merge$CustomerName%in%c("M3D0","M3D3","M3D6")]="M3"
# twinstrand_maf_merge$experiment[twinstrand_maf_merge$CustomerName%in%c("M4D0","M4D3","M4D6")]="M4"
# twinstrand_maf_merge$experiment[twinstrand_maf_merge$CustomerName%in%c("M5D0","M5D3","M5D6")]="M5"
# twinstrand_maf_merge$experiment[twinstrand_maf_merge$CustomerName%in%c("M6D0","M6D3","M6D6")]="M6"
# twinstrand_maf_merge$experiment[twinstrand_maf_merge$CustomerName%in%c("M7D0","M7D3","M7D6")]="M7"
# twinstrand_maf_merge$experiment[twinstrand_maf_merge$CustomerName%in%c("Enu3_D3","Enu3_D6")]="Enu_3"
# twinstrand_maf_merge$experiment[twinstrand_maf_merge$CustomerName%in%c("Enu4_D0","Enu4_D3","Enu4_D6")]="Enu_4" ##Updated this line for ENU
# 
# twinstrand_maf_merge$Spike_in_freq[twinstrand_maf_merge$CustomerName%in%c("M3D0","M3D3","M3D6")]=1000
# twinstrand_maf_merge$Spike_in_freq[twinstrand_maf_merge$CustomerName%in%c("M4D0","M4D3","M4D6")]=5000
# twinstrand_maf_merge$Spike_in_freq[twinstrand_maf_merge$CustomerName%in%c("M5D0","M5D3","M5D6")]=1000
# twinstrand_maf_merge$Spike_in_freq[twinstrand_maf_merge$CustomerName%in%c("M6D0","M6D3","M6D6")]=5000
# twinstrand_maf_merge$Spike_in_freq[twinstrand_maf_merge$CustomerName%in%c("M7D0","M7D3","M7D6")]=1000
# twinstrand_maf_merge$Spike_in_freq[twinstrand_maf_merge$CustomerName%in%c("Enu3_D3","Enu3_D6")]=1000
# twinstrand_maf_merge$Spike_in_freq[twinstrand_maf_merge$CustomerName%in%c("Enu4_D0","Enu4_D3","Enu4_D6")]=1000 ##Updated this line for ENU
# 
# twinstrand_maf_merge$time_point[twinstrand_maf_merge$CustomerName%in%c("M3D0","M6D0","Enu4_D0")]="D0"
# twinstrand_maf_merge$time_point[twinstrand_maf_merge$CustomerName%in%c("M3D3","M4D3","M5D3","M6D3","M7D3","Enu3_D3","Enu4_D3")]="D3"
# twinstrand_maf_merge$time_point[twinstrand_maf_merge$CustomerName%in%c("M3D6","M4D6","M5D6","M6D6","M7D6","Enu3_D6","Enu4_D6")]="D6"
# 
# 
# twinstrand_maf_merge=twinstrand_maf_merge%>%mutate(totalmutant=AltDepth/Depth*totalcells)

ggplot(twinstrand_maf_merge%>%filter(!mutant=="NA",!experiment%in%c("Enu_3","Enu_4")),aes(x=time_point,y=AltDepth,color=factor(experiment)))+geom_point()+facet_wrap(~mutant)+cleanup
#!!!

a=twinstrand_maf_merge%>%dplyr::select(Annotation,CustomerName,experiment,REF,ALT,Depth,AltDepth,mutant)%>%filter(grepl("ENU",Annotation,ignore.case = T),grepl("D0",Annotation,ignore.case = T),experiment=="Enu_4")%>%arrange(desc(AltDepth))
# ggplot(a,aes(x=mutant,y=))#!!!!!!!!Continuefromhere!
# b=twinstrand_maf_merge%>%select(Annotation,CustomerName,experiment,REF,ALT,Depth,AltDepth,mutant)%>%filter(grepl("M6D0",CustomerName,ignore.case = T))%>%arrange(desc(AltDepth))

  plotly=ggplot(twinstrand_maf_merge%>%filter(grepl("ENU",Annotation,ignore.case = T),experiment=="Enu_4"),aes(x=time_point,y=AltDepth,color=factor(experiment)))+geom_point()+facet_wrap(~mutant)+cleanup
  ggplotly(plotly)
sum(a$AltDepth)-20134 ###reads that were resistant clones.
  plotly=ggplot(twinstrand_maf_merge%>%filter(grepl("ENU",Annotation,ignore.case = T),experiment=="Enu_3"),aes(x=time_point,y=AltDepth,color=factor(experiment)))+geom_point()+facet_wrap(~mutant)+cleanup
  ggplotly(plotly)
  
###The main thing I'm realizing from the ENU data is that the more frequent mutants DEFINITELY start to dominate during the latter days. Most resistant mutants have a lower depth of coverage later into the days. Only the mutants of highest resistance like T315I and G250E actually have an increase in MAF.
a=twinstrand_maf_merge%>%filter(tki_resistant_mutation=="True",!mutant=="NA",Spike_in_freq==1000,experiment%in%c("Enu_3","Enu_4"))
plotly=ggplot(twinstrand_maf_merge%>%filter(tki_resistant_mutation=="True",!mutant=="NA",Spike_in_freq==1000,experiment%in%c("Enu_3","Enu_4")),aes(x=time_point,y=totalmutant,color=factor(experiment)))+geom_point()+facet_wrap(~mutant)+scale_y_continuous(trans = "log10")+cleanup
ggplotly(plotly)
```


Generating mean growth rate across mutants to see if that improves clinical abundance predictions. Short answer: no it doesn't based on our current specs
```{r}
a=twinstrand_simple_melt_merge%>%
  mutate(netgr_obs=case_when(experiment=="M5"~netgr_obs+.015,
                                   experiment%in%c("M3","M6","M5","M4","M7")~netgr_obs))

a_new=a%>%filter(experiment%in%c("M3"),duration%in%("d3d6"))
a_new=a_new%>%filter(!netgr_obs%in%NA)%>%
  dplyr::select(mutant,netgr_obs)

# mean_netgr=twinstrand_simple_melt_merge%>%group_by(mutant)%>%summarize(netgr_pred=mean(netgr_obs,na.rm=T))
# a_new=mean_netgr

mean_netgr=twinstrand_simple_melt_merge%>%group_by(mutant)%>%summarize(netgr_mean=mean(netgr_obs,na.rm=T))
a_new=mean_netgr
```

Checking if ENU mutants follow expected IC50s
```{r}
enu_plots=twinstrand_simple_melt_merge%>%filter(experiment%in%c("Enu_4","Enu_3"),duration%in%"d3d6")
#hardcoding adjustments to the growth rates
enu_plots$netgr_obs[enu_plots$experiment=="Enu_3"]=enu_plots$netgr_obs[enu_plots$experiment=="Enu_3"]-.011

plotly=ggplot(enu_plots,aes(x=netgr_pred,y=netgr_obs,label=mutant))+geom_text()+facet_wrap(~experiment)+geom_abline()+cleanup
ggplotly(plotly)
plotly=ggplot(enu_plots,aes(x=netgr_pred,y=netgr_obs,label=mutant,fill=factor(experiment)))+geom_text()+geom_abline()+cleanup
ggplotly(plotly)
```
